---
title: "2022_06_14_assign_dominant_barcodes"
output: html_notebook
---
#Set working directory to appropriate folder for inputs and outputs on Google Drive
```{r, setup, include=FALSE}

knitr::opts_knit$set(root.dir = '/Volumes/GoogleDrive/My Drive/Fasse_Shared/AJF_Drive_copy/Experiments/AJF009') # for aria's computer
#knitr::opts_knit$set(root.dir = '/Volumes/GoogleDrive/.shortcut-targets-by-id/1zSqx3IzXMwt6clUjwyqmlOf4G1K53lvy/Fasse_Shared/AJF_Drive_copy/Experiments/AJF009') # for dylan's computer

#2022_01_14_analysis_scripts/2022_05_27_analysis/Assign_dominant_barcodes is additional path for outputs

```

# Assign the dominant lineage (if there) to each cell
# Will be using the count cutoff that gives the largest delta between the number of cells with a single barcode vs multiple barcodes
```{r include = FALSE}
# Initialize ----
rm(list = ls())
gc()
library(dplyr)
library(Seurat)
library(ggplot2)
library(RColorBrewer)
library(kit)
`%nin%` = Negate(`%in%`)
```

# Assign directory and load files
```{r include = FALSE}

load('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/all_data_merged.RData') #for merged object
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/Objects_premerged.RData') #for individual objects
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/dabtram_both_times.RData')

reference <- read.delim('2022_05_19_Barcode_outputs/CellRanger_inputs/FeatureReference_filtered.csv')

load('2022_01_14_analysis_scripts/2022_05_27_analysis/Test_barcode_assignment/lineage_count_cutoffs.RData') #lineage count cutoffs from test_barcode_assignment

rm(cistocis, cistococl2, cistodabtram, cocl2tocis, cocl2tococl2, cocl2todabtram, dabtramtocis, dabtramtococl2, dabtramtodabtram) # only need the first drug objects
```

# Build counts object
```{r include = FALSE}
counts <- GetAssayData(all_data, assay = 'lineage')
num_lin_orig <- nrow(counts)
```

# Remove all lineages with only one count across all cells
```{r include = FALSE}
counts_filt <- counts[which(rowSums(counts) > 1),] # Only care about lineages that have greater than one total count
num_lin_filt <- nrow(counts_filt)
percent_lin_filt <- num_lin_filt/num_lin_orig*100

df_counts <- as.data.frame(counts_filt)
```

# Find number of barcodes per cell with nonzero counts
```{r}
barcodes_per_cell <- apply(counts_filt,2, function(x) sum(x>0))
barcodes_per_cell_table <- table(barcodes_per_cell)
barcodes_per_cell_table
```

# filter based on the maximum number of cells with one lineage
```{r}
filter_max_single <- cutoffs$Max_single
names(filter_max_single) <- rownames(cutoffs)

fam_max_single <- list()
for (k in names(filter_max_single)){
  for (i in grep(k,colnames(df_counts))){
    fam_max_single[[i]] <- rownames(df_counts)[which(df_counts[,i] > filter_max_single[k])]
  }
}
```

# Look through cells that still have multiple barcodes and see if any have one with much higher expression than the rest ----
```{r}
# Build a boolean of the cells that still have multiple barcodes
boolean_multi_lin <- lengths(fam_max_single)>1

# Assign dominant barcode if the number of counts in the highest expressed barcodes is >triple that of second highest barcode
fixed_multi<- list()
for (i in (1:ncol(df_counts))){ 
  if ( boolean_multi_lin[i] == T) {
    if(df_counts[topn(as.numeric(df_counts[,i]),2),i][1] >= 3*df_counts[topn(as.numeric(df_counts[,i]),2),i][2]){
      fixed_multi[[i]] <- rownames(df_counts)[topn(as.numeric(df_counts[,i]),2)][1]
    }else{
      fixed_multi[[i]] <- "Still multiple"
    }
  } else{ fixed_multi[[i]] <- "Single"
  }
}

# Replace the values in fam that had 2+ barcodes with with either the dominant barcode if found or say that its still multiple
fam_multi_collapse <- fam_max_single
fam_multi_collapse[boolean_multi_lin] <- fixed_multi[boolean_multi_lin]

fam_multi_collapse[lengths(fam_multi_collapse) == 0] <- 'No Barcode'
```

# Write this to metadata
```{r}
lin_meta <- t(as.data.frame(fam_multi_collapse))
colnames(lin_meta) <- 'Lineage'
rownames(lin_meta) <- colnames(df_counts)
all_data$Lineage <- lin_meta
```

# Save the updated all_data object
```{r}
save(all_data, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Assign_dominant_barcodes/all_data_final_lineages.RData')
```


# Load in the first drug only objects and add the lineage information pulled from all_data
```{r}

condition_indices <- list()
for (i in unique(all_data$OG_condition)){
  condition_indices[[paste0(i, '_inds')]] <- grep(i, names(all_data$Lineage))
}

# now need to remove indices from the first lists that are incorrectly assigned based on a shared name

#dabtram first, minus other things that have dabtram in name
condition_indices$dabtram_both_times_inds <- condition_indices$dabtram_inds[condition_indices$dabtram_inds %nin% c(condition_indices$dabtramtococl2_inds, condition_indices$dabtramtocis_inds, condition_indices$cocl2todabtram_inds, condition_indices$cistodabtram_inds)]
dabtram_both_times$Lineage <- all_data$Lineage[condition_indices$dabtram_both_times_inds]
save(dabtram_both_times, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Assign_dominant_barcodes/dabtram_both_times_final_lineages.RData')

condition_indices$dabtram_inds <- condition_indices$dabtram_inds[condition_indices$dabtram_inds %nin% c(condition_indices$dabtramtodabtram_inds, condition_indices$dabtramtococl2_inds, condition_indices$dabtramtocis_inds, condition_indices$cocl2todabtram_inds, condition_indices$cistodabtram_inds)]
dabtram$Lineage <- all_data$Lineage[condition_indices$dabtram_inds]
save(dabtram, file = "2022_01_14_analysis_scripts/2022_05_27_analysis/Assign_dominant_barcodes/dabtram_final_lineages.RData")

# cocl2 first, minus other things that have cocl2 in name
condition_indices$cocl2_inds <- condition_indices$cocl2_inds[condition_indices$cocl2_inds %nin% c(condition_indices$dabtramtococl2_inds, condition_indices$cocl2todabtram_inds, condition_indices$cocl2tococl2_inds, condition_indices$cocl2tocis_inds, condition_indices$cistococl2_inds)]
cocl2$Lineage <- all_data$Lineage[condition_indices$cocl2_inds]
save(cocl2, file = "2022_01_14_analysis_scripts/2022_05_27_analysis/Assign_dominant_barcodes/cocl2_final_lineages.RData")

# cis first, minus other things that have cis in name
condition_indices$cis_inds <- condition_indices$cis_inds[condition_indices$cis_inds %nin% c(condition_indices$dabtramtocis_inds, condition_indices$cocl2tocis_inds, condition_indices$cistodabtram_inds, condition_indices$cistococl2_inds, condition_indices$cistocis_inds)]
cis$Lineage <- all_data$Lineage[condition_indices$cis_inds]
save(cis, file = "2022_01_14_analysis_scripts/2022_05_27_analysis/Assign_dominant_barcodes/cis_final_lineages.RData")

#can check that above worked using below chunk

#test <- data.frame (cell = names(dabtram_both_times$orig.ident), lineage_dt = dabtram_both_times$Lineage[names(dabtram_both_times$orig.ident)], lineage_alldata = all_data$Lineage[names(dabtram_both_times$orig.ident)])

#this confirms that above indexing results in the same lineage assignments for dabtram_both_times as in all_data object

```

