---
title: "R Notebook"
output: html_notebook
---
#IMPORTANT NOTE: everything for plotting in figures currently comes from the second_timepoint object, but there are additional chunks that run similar analyses on all_data objects with different cluster numbers


#Set working directory to appropriate folder for inputs and outputs on Google Drive
```{r, setup, include=FALSE}
#knitr::opts_knit$set(root.dir = '/Volumes/GoogleDrive/My Drive/Fasse_Shared/AJF_Drive_copy/Experiments/AJF009') # for aria's computer
knitr::opts_knit$set(root.dir = '/Users/dylanschaff/Library/CloudStorage/GoogleDrive-dyschaff@sydshafferlab.com/My Drive/Fasse_Shared/AJF_Drive_copy/Experiments/AJF009') # for dylan's computer

#2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/ is additional path for outputs

```

#Initialize
```{r include = FALSE}
rm(list = ls())
library(dplyr)
library(Seurat)
library(ggplot2)
library(RColorBrewer)
library(xlsx)
```

# Load data
```{r}
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/Objects_premerged.RData')
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/second_timepoint_merged.RData')
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/first_timepoint_merged.RData')
```

# cluster second timepoint and plot
```{r}
second_timepoint <- NormalizeData(second_timepoint)
second_timepoint <- FindVariableFeatures(second_timepoint, selection.method = 'vst', nFeatures = 20000)
second_timepoint <- ScaleData(second_timepoint)
second_timepoint <- RunPCA(second_timepoint)
second_timepoint <- FindNeighbors(second_timepoint, dims = 1:15)
second_timepoint <- FindClusters(second_timepoint, resolution = 0.5)
second_timepoint <- RunUMAP(second_timepoint, dims = 1:15)

cells_per_cluster <- data.frame (Cluster = as.numeric(second_timepoint$seurat_clusters), Condition = second_timepoint$OG_condition)
cells_per_cluster_list <- list()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/original_condition_second_timepoint.pdf')
print(DimPlot(second_timepoint))
print(DimPlot(second_timepoint, label = T, group.by = 'OG_condition', cols = c('dabtramtodabtram' = '#561E59', 'dabtramtococl2' = '#A2248E', 'dabtramtocis' = '#9D85BE', 'cocl2todabtram' = '#10413B', 'cocl2tococl2' = '#6ABD45', 'cocl2tocis' = '#6DC49C', 'cistodabtram' = '#A23622', 'cistococl2' = '#F49129', 'cistocis' = '#FBD08C')))

for (i in 1:(max(cells_per_cluster$Cluster))){
  currentcluster <- filter(cells_per_cluster, cells_per_cluster$Cluster == i)
  cells_per_cluster_list[[paste0('Cluster', i)]] <- data.frame(table(currentcluster$Condition))
  
  print(ggplot(cells_per_cluster_list[[paste0('Cluster', i)]], aes(x ='', y = Freq, fill = Var1)) + geom_bar(stat = 'identity') + coord_polar('y', start = 0) + theme_void() + scale_fill_manual(values = c('dabtramtodabtram' = '#561E59', 'dabtramtococl2' = '#A2248E', 'dabtramtocis' = '#9D85BE', 'cocl2todabtram' = '#10413B', 'cocl2tococl2' = '#6ABD45', 'cocl2tocis' = '#6DC49C', 'cistodabtram' = '#A23622', 'cistococl2' = '#F49129', 'cistocis' = '#FBD08C')) + labs(title = paste('Original condition of cells in cluster', i-1)))
}
dev.off()

```

# This is the same chunk as above but it makes the plots as bar charts in individual PDFs for pulling into illustrator
```{r}

cells_per_cluster <- data.frame (Cluster = as.numeric(second_timepoint$seurat_clusters), Condition = second_timepoint$OG_condition)
cells_per_cluster_list <- list()

for (i in 1:(max(cells_per_cluster$Cluster))){
  pdf(paste0('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/original_condition_second_timepoint_cluster', i-1, '.pdf'))
  currentcluster <- filter(cells_per_cluster, cells_per_cluster$Cluster == i)
  cells_per_cluster_list[[paste0('Cluster', i)]] <- data.frame(table(currentcluster$Condition))
  
  print(ggplot(cells_per_cluster_list[[paste0('Cluster', i)]], aes(x ='', y = Freq, fill = Var1)) + geom_bar(position = 'fill', stat = 'identity') + scale_fill_manual(values = c('dabtram' = '#623594', 'cocl2' = '#0F8241', 'cis' = '#C96D29', 'dabtramtodabtram' = '#561E59', 'dabtramtococl2' = '#A2248E', 'dabtramtocis' = '#9D85BE', 'cocl2todabtram' = '#10413B', 'cocl2tococl2' = '#6ABD45', 'cocl2tocis' = '#6DC49C', 'cistodabtram' = '#A23622', 'cistococl2' = '#F49129', 'cistocis' = '#FBD08C')) + labs(title = paste('Original condition of cells in second timepoint cluster', i-1)))
  dev.off()
}
```

#editing cells_per_cluster so that the condition name is whatever second condition
```{r include = FALSE}

cells_per_cluster_seconddrug <- cells_per_cluster
cells_per_cluster_firstdrug <- cells_per_cluster

for (i in 1:nrow(cells_per_cluster)){
  if (cells_per_cluster$Condition[[i]] == "dabtramtodabtram" || cells_per_cluster$Condition[[i]] == "cistodabtram" || cells_per_cluster$Condition[[i]] == "cocl2todabtram") {
    cells_per_cluster_seconddrug$Condition[[i]] <- "dabtramsecond"
  }
  if (cells_per_cluster$Condition[[i]] == "cocl2tococl2" || cells_per_cluster$Condition[[i]] == "cistococl2" || cells_per_cluster$Condition[[i]] == "dabtramtococl2") {
    cells_per_cluster_seconddrug$Condition[[i]] <- "cocl2second"
  }
  if (cells_per_cluster$Condition[[i]] == "cistocis" || cells_per_cluster$Condition[[i]] == "cocl2tocis" || cells_per_cluster$Condition[[i]] == "dabtramtocis") {
    cells_per_cluster_seconddrug$Condition[[i]] <- "cissecond"
  }
}

for (i in 1:nrow(cells_per_cluster)){
  if (cells_per_cluster$Condition[[i]] == "dabtramtodabtram" || cells_per_cluster$Condition[[i]] == "dabtramtocis" || cells_per_cluster$Condition[[i]] == "dabtramtococl2") {
    cells_per_cluster_firstdrug$Condition[[i]] <- "dabtramfirst"
  }
  if (cells_per_cluster$Condition[[i]] == "cocl2tococl2" || cells_per_cluster$Condition[[i]] == "cocl2tocis" || cells_per_cluster$Condition[[i]] == "cocl2todabtram") {
    cells_per_cluster_firstdrug$Condition[[i]] <- "cocl2first"
  }
  if (cells_per_cluster$Condition[[i]] == "cistocis" || cells_per_cluster$Condition[[i]] == "cistococl2" || cells_per_cluster$Condition[[i]] == "cistodabtram") {
    cells_per_cluster_firstdrug$Condition[[i]] <- "cisfirst"
  }
}

#now colored based on second drug only
for (i in 1:(max(cells_per_cluster_seconddrug$Cluster))){
  pdf(paste0('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/end_condition_second_timepoint', i-1, '.pdf'))
  currentcluster <- filter(cells_per_cluster_seconddrug, cells_per_cluster_seconddrug$Cluster == i)
  cells_per_cluster_list[[paste0('Cluster', i)]] <- data.frame(table(currentcluster$Condition))
  
  print(ggplot(cells_per_cluster_list[[paste0('Cluster', i)]], aes(x ='', y = Freq, fill = Var1)) + geom_bar(position = 'fill', stat = 'identity') + scale_fill_manual(values = c('dabtramsecond' = '#623594', 'cocl2second' = '#0F8241', 'cissecond' = '#C96D29')) + labs(title = paste('End condition of cells in second timepoint cluster', i-1)))
  dev.off()
}

#now colored based on first drug only
for (i in 1:(max(cells_per_cluster_firstdrug$Cluster))){
  pdf(paste0('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/first_condition_second_timepoint', i-1, '.pdf'))
  currentcluster <- filter(cells_per_cluster_firstdrug, cells_per_cluster_firstdrug$Cluster == i)
  cells_per_cluster_list[[paste0('Cluster', i)]] <- data.frame(table(currentcluster$Condition))
  
  print(ggplot(cells_per_cluster_list[[paste0('Cluster', i)]], aes(x ='', y = Freq, fill = Var1)) + geom_bar(position = 'fill', stat = 'identity') + scale_fill_manual(values = c('dabtramfirst' = '#623594', 'cocl2first' = '#0F8241', 'cisfirst' = '#C96D29')) + labs(title = paste('End condition of cells in first timepoint cluster', i-1)))
  dev.off()
}
```

#UMAPs highlighting all cells that had same first and second drug in second_timepoint object
```{r}
cells_per_condition <- list()
for (i in c('dabtramtodabtram', 'dabtramtococl2', 'dabtramtocis', 'cocl2todabtram', 'cocl2tococl2', 'cocl2tocis', 'cistodabtram', 'cistococl2', 'cistocis')){
  cells_per_condition[[paste0(i, '_cells')]] <- names(second_timepoint$orig.ident[second_timepoint$OG_condition == i])
}

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/drug_group_highlights.pdf')

DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$dabtramtodabtram_cells, cells_per_condition$dabtramtocis_cells, cells_per_condition$dabtramtococl2_cells),
        cols.highlight = ('red')) + ggtitle('dabtram first cells')
DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$cocl2tococl2_cells, cells_per_condition$cocl2tocis_cells, cells_per_condition$cocl2todabtram_cells),
        cols.highlight = ('red')) + ggtitle('cocl2 first cells')
DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$cis_cells, cells_per_condition$cistocis_cells, cells_per_condition$cistococl2_cells, cells_per_condition$cistodabtram_cells),
        cols.highlight = ('red')) + ggtitle('cis first cells')

DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$dabtramtodabtram_cells, cells_per_condition$cistodabtram_cells, cells_per_condition$cocl2todabtram_cells),
        cols.highlight = ('blue')) + ggtitle('dabtram second cells')
DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$cocl2tococl2_cells, cells_per_condition$cistococl2_cells, cells_per_condition$dabtramtococl2_cells),
        cols.highlight = ('blue')) + ggtitle('cocl2 second cells')
DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$cis_cells, cells_per_condition$cistocis_cells, cells_per_condition$cocl2tocis_cells, cells_per_condition$dabtramtocis_cells),
        cols.highlight = ('blue')) + ggtitle('cis second cells')

dev.off()
```

#UMAPs highlighting all cells that had same first drug in first_timepoint object
```{r}
pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/drug_group_highlights_first_timepoint.pdf')

DimPlot(first_timepoint, reduction = "umap", dims = c(1,2), group.by = "OG_condition", pt.size = 2, cols =  c('dabtram' = '#623594', 'cocl2' = '#0F8241', 'cis' = '#C96D29'))
DimPlot(first_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(names(first_timepoint$orig.ident[first_timepoint$OG_condition == 'dabtram'])),
        cols.highlight = ('red')) + ggtitle('dabtram first cells')
DimPlot(first_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(names(first_timepoint$orig.ident[first_timepoint$OG_condition == 'cocl2'])),
        cols.highlight = ('red')) + ggtitle('cocl2 first cells')
DimPlot(first_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(names(first_timepoint$orig.ident[first_timepoint$OG_condition == 'cis'])),
        cols.highlight = ('red')) + ggtitle('cis first cells')

FeaturePlot(first_timepoint, features = 'EGFR', pt.size = 2) +
  scale_colour_gradientn(colors = rev(brewer.pal(n = 11, name = 'RdBu')))
FeaturePlot(first_timepoint, features = 'NGFR', pt.size = 2) +
  scale_colour_gradientn(colors = rev(brewer.pal(n = 11, name = 'RdBu')))


dev.off()
```

#More plots not in PDF but just for quick visualizations
```{r}
DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$dabtramtodabtram_cells, cells_per_condition$dabtramtocis_cells, cells_per_condition$dabtramtococl2_cells),
        cols.highlight = c('#a2248e', '#9d85be', '#561e59')) + ggtitle('dabtram first cells')

DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$dabtramtodabtram_cells, cells_per_condition$dabtramtocis_cells, cells_per_condition$dabtramtococl2_cells),
        cols.highlight = ('#623594')) + ggtitle('dabtram first cells')

DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$dabtramtodabtram_cells, cells_per_condition$cistodabtram_cells, cells_per_condition$cocl2todabtram_cells),
        cols.highlight = c('#10413b', '#a23622', '#561e59')) + ggtitle('dabtram second cells')

DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$dabtramtodabtram_cells, cells_per_condition$cistodabtram_cells, cells_per_condition$cocl2todabtram_cells),
        cols.highlight = ('#623594')) + ggtitle('dabtram second cells')

```

```{r}
DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$cocl2tococl2_cells, cells_per_condition$cocl2tocis_cells, cells_per_condition$cocl2todabtram_cells),
        cols.highlight = c('#10413b', '#6dc49c', '#6abd45')) + ggtitle('cocl2 first cells')

DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$cocl2tococl2_cells, cells_per_condition$cocl2tocis_cells, cells_per_condition$cocl2todabtram_cells),
        cols.highlight = ('#0f8241')) + ggtitle('cocl2 first cells')

DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$cocl2tococl2_cells, cells_per_condition$cistococl2_cells, cells_per_condition$dabtramtococl2_cells),
        cols.highlight = c('#a2248e', '#f49129', '#6abd45')) + ggtitle('cocl2 second cells')

DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$cocl2tococl2_cells, cells_per_condition$cistococl2_cells, cells_per_condition$dabtramtococl2_cells),
        cols.highlight = ('#0f8241')) + ggtitle('cocl2 second cells')

```

```{r}
DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$cis_cells, cells_per_condition$cistocis_cells, cells_per_condition$cistococl2_cells, cells_per_condition$cistodabtram_cells),
        cols.highlight = c('#a23622', '#f49129', '#fbd08c')) + ggtitle('cis first cells')

DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$cis_cells, cells_per_condition$cistocis_cells, cells_per_condition$cistococl2_cells, cells_per_condition$cistodabtram_cells),
        cols.highlight = ('#c96d29')) + ggtitle('cis first cells')

DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$cis_cells, cells_per_condition$cistocis_cells, cells_per_condition$cocl2tocis_cells, cells_per_condition$dabtramtocis_cells),
        cols.highlight = c('#9d85be', '#6dc49c', '#fbd08c')) + ggtitle('cis second cells')

DimPlot(second_timepoint, reduction = "umap", dims = c(1,2), group.by = 'OG_condition', pt.size = .1,
        cells.highlight = list(cells_per_condition$cis_cells, cells_per_condition$cistocis_cells, cells_per_condition$cocl2tocis_cells, cells_per_condition$dabtramtocis_cells),
        cols.highlight = ('#c96d29')) + ggtitle('cis second cells')

```

# Save the object to load in for distance metrics
```{r}
save.image('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/workspace.RData')
```

# Run distance metrics
```{r}
# Define manhatten distance function
manhattan.distance <- function(x, y) return(sum(abs(x-y)))

# Make metadata objects of the first and second conditions
second_timepoint$first_treatment <- sapply(strsplit(second_timepoint$OG_condition, "to"), "[[", 1)
second_timepoint$second_treatment <- sapply(strsplit(second_timepoint$OG_condition, "to"), "[[", 2)

# Get input data and subest
input_data <- GetAssayData(second_timepoint, assay = 'RNA', slot = 'scale.data')

# Number of cells for subsetting
num_cells <- 10000

# Look at grouping based on first sample
Idents(second_timepoint) <- second_timepoint$first_treatment
DimPlot(second_timepoint)

cocl2_first_cells <-  sample(names(second_timepoint$first_treatment)[second_timepoint$first_treatment == 'cocl2'], num_cells)
cocl2_first_subset <- input_data[,cocl2_first_cells]
cocl2_first_manhatten_distance <- CustomDistance(cocl2_first_subset, manhattan.distance)

dabtram_first_cells <-  sample(names(second_timepoint$first_treatment)[second_timepoint$first_treatment == 'dabtram'], num_cells)
dabtram_first_subset <- input_data[,dabtram_first_cells]
dabtram_first_manhatten_distance <- CustomDistance(dabtram_first_subset, manhattan.distance)

cis_first_cells <-  sample(names(second_timepoint$first_treatment)[second_timepoint$first_treatment == 'cis'], num_cells)
cis_first_subset <- input_data[,cis_first_cells]
cis_first_manhatten_distance <- CustomDistance(cis_first_subset, manhattan.distance)

Idents(second_timepoint) <- second_timepoint$second_treatment
DimPlot(second_timepoint)

cocl2_second_cells <-  sample(names(second_timepoint$second_treatment)[second_timepoint$second_treatment == 'cocl2'], num_cells)
cocl2_second_subset <- input_data[,cocl2_second_cells]
cocl2_second_manhatten_distance <- CustomDistance(cocl2_second_subset, manhattan.distance)

dabtram_second_cells <-  sample(names(second_timepoint$second_treatment)[second_timepoint$second_treatment == 'dabtram'], num_cells)
dabtram_second_subset <- input_data[,dabtram_second_cells]
dabtram_second_manhatten_distance <- CustomDistance(dabtram_second_subset, manhattan.distance)

cis_second_cells <-  sample(names(second_timepoint$second_treatment)[second_timepoint$second_treatment == 'cis'], num_cells)
cis_second_subset <- input_data[,cis_second_cells]
cis_second_manhatten_distance <- CustomDistance(cis_second_subset, manhattan.distance)

plotting_df <- data.frame(Grouping = c(rep('first',3*length(cis_first_manhatten_distance)),rep('second', 3*(length(cis_second_manhatten_distance)))),
                          Manhatten_dist <- c(cocl2_first_manhatten_distance, dabtram_first_manhatten_distance, cis_first_manhatten_distance, cocl2_second_manhatten_distance,dabtram_second_manhatten_distance, cis_second_manhatten_distance),
                          Treatment = c(rep('CoCl2 first',length(cocl2_first_manhatten_distance)),rep('Dab/Tram first',length(dabtram_first_manhatten_distance)),rep('Cisplatin first',length(cis_first_manhatten_distance)),rep('CoCl2 second',length(cocl2_second_manhatten_distance)),rep('Dab/Tram second',length(dabtram_second_manhatten_distance)),rep('Cisplatin second',length(cis_second_manhatten_distance))))

ggplot(plotting_df, aes(x = Treatment, y = Manhatten_dist, fill = Grouping)) + geom_violin() + geom_boxplot(width = 0.1)

save.image('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/workspace_v2.RData')

```

# Run pearson - https://pubmed.ncbi.nlm.nih.gov/30137247/
```{r}

#load('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/workspace_v2.RData')

rm(manhatten.distance, cocl2_first_manhatten_distance, dabtram_first_manhatten_distance, cis_first_manhatten_distance, cocl2_second_manhatten_distance, dabtram_second_manhatten_distance, cis_second_manhatten_distance)
rm(cis, cistocis, cistococl2, cistodabtram, cocl2, cocl2tocis, cocl2tococl2, cocl2todabtram, dabtram, dabtramtocis, dabtramtococl2, dabtramtodabtram)
gc()

# Make metadata objects of the first and second conditions
second_timepoint$first_treatment <- sapply(strsplit(second_timepoint$OG_condition, "to"), "[[", 1)
second_timepoint$second_treatment <- sapply(strsplit(second_timepoint$OG_condition, "to"), "[[", 2)

# Get input data and subest
input_data <- GetAssayData(second_timepoint, assay = 'RNA', slot = 'scale.data')


# Look at grouping based on first sample - does not actually subset.
Idents(second_timepoint) <- second_timepoint$first_treatment
DimPlot(second_timepoint)

cocl2_first_cells <-  names(second_timepoint$first_treatment)[second_timepoint$first_treatment == 'cocl2']
cocl2_first_subset <- input_data[,cocl2_first_cells]
cocl2_first_pearson <- cor(cocl2_first_subset)
cocl2_first_pearson_filt <- cocl2_first_pearson[lower.tri(cocl2_first_pearson, diag = FALSE)]

set.seed(1)
cocl2_first_subset_rand <- input_data[,sample(colnames(input_data),length(cocl2_first_cells))]
cocl2_first_pearson_rand <- cor(cocl2_first_subset_rand)
cocl2_first_pearson_filt_rand <- cocl2_first_pearson_rand[lower.tri(cocl2_first_pearson_rand, diag = FALSE)]

dabtram_first_cells <-  names(second_timepoint$first_treatment)[second_timepoint$first_treatment == 'dabtram']
dabtram_first_subset <- input_data[,dabtram_first_cells]
dabtram_first_pearson <- cor(dabtram_first_subset)
dabtram_first_pearson_filt <- dabtram_first_pearson[lower.tri(dabtram_first_pearson, diag = FALSE)]

set.seed(1)
dabtram_first_subset_rand <- input_data[,sample(colnames(input_data),length(dabtram_first_cells))]
dabtram_first_pearson_rand <- cor(dabtram_first_subset_rand)
dabtram_first_pearson_filt_rand <- dabtram_first_pearson_rand[lower.tri(dabtram_first_pearson_rand, diag = FALSE)]

cis_first_cells <-  names(second_timepoint$first_treatment)[second_timepoint$first_treatment == 'cis']
cis_first_subset <- input_data[,cis_first_cells]
cis_first_pearson <- cor(cis_first_subset)
cis_first_pearson_filt <- cis_first_pearson[lower.tri(cis_first_pearson, diag = FALSE)]

set.seed(1)
cis_first_subset_rand <- input_data[,sample(colnames(input_data),length(cis_first_cells))]
cis_first_pearson_rand <- cor(cis_first_subset_rand)
cis_first_pearson_filt_rand <- cis_first_pearson_rand[lower.tri(cis_first_pearson_rand, diag = FALSE)]

Idents(second_timepoint) <- second_timepoint$second_treatment
DimPlot(second_timepoint)

cocl2_second_cells <-  names(second_timepoint$second_treatment)[second_timepoint$second_treatment == 'cocl2']
cocl2_second_subset <- input_data[,cocl2_second_cells]
cocl2_second_pearson <- cor(cocl2_second_subset)
cocl2_second_pearson_filt <- cocl2_second_pearson[lower.tri(cocl2_second_pearson, diag = FALSE)]

set.seed(1)
cocl2_second_subset_rand <- input_data[,sample(colnames(input_data),length(cocl2_second_cells))]
cocl2_second_pearson_rand <- cor(cocl2_second_subset_rand)
cocl2_second_pearson_filt_rand <- cocl2_second_pearson_rand[lower.tri(cocl2_second_pearson_rand, diag = FALSE)]

dabtram_second_cells <-  names(second_timepoint$second_treatment)[second_timepoint$second_treatment == 'dabtram']
dabtram_second_subset <- input_data[,dabtram_second_cells]
dabtram_second_pearson <- cor(dabtram_second_subset)
dabtram_second_pearson_filt <- dabtram_second_pearson[lower.tri(dabtram_second_pearson, diag = FALSE)]

set.seed(1)
dabtram_second_subset_rand <- input_data[,sample(colnames(input_data),length(dabtram_second_cells))]
dabtram_second_pearson_rand <- cor(dabtram_second_subset_rand)
dabtram_second_pearson_filt_rand <- dabtram_second_pearson_rand[lower.tri(dabtram_second_pearson_rand, diag = FALSE)]

cis_second_cells <-  names(second_timepoint$second_treatment)[second_timepoint$second_treatment == 'cis']
cis_second_subset <- input_data[,cis_second_cells]
cis_second_pearson <- cor(cis_second_subset)
cis_second_pearson_filt <- cis_second_pearson[lower.tri(cis_second_pearson, diag = FALSE)]

set.seed(1)
cis_second_subset_rand <- input_data[,sample(colnames(input_data),length(cis_second_cells))]
cis_second_pearson_rand <- cor(cis_second_subset_rand)
cis_second_pearson_filt_rand <- cis_second_pearson_rand[lower.tri(cis_second_pearson_rand, diag = FALSE)]

save.image('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/workspace_v3.RData')

# Save CoCl2 outputs
save(cocl2_first_pearson, cocl2_first_pearson_rand, cocl2_first_subset, cocl2_first_subset_rand, cocl2_first_pearson_filt, cocl2_first_pearson_filt_rand, cocl2_second_pearson, cocl2_second_pearson_rand, cocl2_second_subset, cocl2_second_subset_rand, cocl2_second_pearson_filt, cocl2_second_pearson_filt_rand, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/cocl2_pearson_results.RData')
rm(cocl2_first_pearson, cocl2_first_pearson_rand, cocl2_first_subset, cocl2_first_subset_rand, cocl2_first_pearson_filt, cocl2_first_pearson_filt_rand, cocl2_second_pearson, cocl2_second_pearson_rand, cocl2_second_subset, cocl2_second_subset_rand, cocl2_second_pearson_filt, cocl2_second_pearson_filt_rand)

# Save dabtram outputs
save(dabtram_first_pearson, dabtram_first_pearson_rand, dabtram_first_subset, dabtram_first_subset_rand, dabtram_first_pearson_filt, dabtram_first_pearson_filt_rand, dabtram_second_pearson, dabtram_second_pearson_rand, dabtram_second_subset, dabtram_second_subset_rand, dabtram_second_pearson_filt, dabtram_second_pearson_filt_rand, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/dabtram_pearson_results.RData')
rm(dabtram_first_pearson, dabtram_first_pearson_rand, dabtram_first_subset, dabtram_first_subset_rand, dabtram_first_pearson_filt, dabtram_first_pearson_filt_rand, dabtram_second_pearson, dabtram_second_pearson_rand, dabtram_second_subset, dabtram_second_subset_rand, dabtram_second_pearson_filt, dabtram_second_pearson_filt_rand)

# Save cis outputs
save(cis_first_pearson, cis_first_pearson_rand, cis_first_subset, cis_first_subset_rand, cis_first_pearson_filt, cis_first_pearson_filt_rand, cis_second_pearson, cis_second_pearson_rand, cis_second_subset, cis_second_subset_rand, cis_second_pearson_filt, cis_second_pearson_filt_rand, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/cis_pearson_results.RData')
rm(cis_first_pearson, cis_first_pearson_rand, cis_first_subset, cis_first_subset_rand, cis_first_pearson_filt, cis_first_pearson_filt_rand, cis_second_pearson, cis_second_pearson_rand, cis_second_subset, cis_second_subset_rand, cis_second_pearson_filt, cis_second_pearson_filt_rand)
```

# Statistical analysis and plotting of pearson metrics - CoCl2
```{r}
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/cocl2_pearson_results.RData') # Load data

pearson_ttest_cocl2_firstvsrand <- t.test(cocl2_first_pearson_filt, cocl2_first_pearson_filt_rand,  paired = F)
pearson_ttest_cocl2_secondvsrand <- t.test(cocl2_second_pearson_filt, cocl2_second_pearson_filt_rand,  paired = F)
pearson_ttest_cocl2_secondvsfirst <- t.test(cocl2_second_pearson_filt, cocl2_first_pearson_filt,  paired = F)
pearson_ttest_cocl2_randvsrand <- t.test(cocl2_second_pearson_filt_rand, cocl2_first_pearson_filt_rand,  paired = F)

rm(cocl2_first_pearson, cocl2_first_pearson_rand, cocl2_first_subset, cocl2_first_subset_rand, cocl2_second_pearson, cocl2_second_pearson_rand, cocl2_second_subset, cocl2_second_subset_rand)

plotting_df_pearson_cocl2 <- data.frame(Grouping = c(rep('first',length(cocl2_first_pearson_filt)), rep('random',length(cocl2_first_pearson_filt)), rep('second', length(cocl2_second_pearson_filt)), rep('random', length(cocl2_second_pearson_filt))),
                          Pearson = c(cocl2_first_pearson_filt, cocl2_first_pearson_filt_rand, cocl2_second_pearson_filt, cocl2_second_pearson_filt_rand),
                          Treatment = c(rep('CoCl2 first',length(cocl2_first_pearson_filt)), rep('CoCl2 first rand', length(cocl2_first_pearson_filt_rand)),rep('CoCl2 second',length(cocl2_second_pearson_filt)),rep('CoCl2 second rand',length(cocl2_second_pearson_filt_rand))))
colnames(plotting_df_pearson_cocl2) <- c('Grouping','Pearson','Treatment')

rm(cocl2_first_pearson_filt, cocl2_first_pearson_filt_rand, cocl2_second_pearson_filt, cocl2_second_pearson_filt_rand)
gc()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/cocl2_pearson_plot_subsampled.pdf')
set.seed(1)
ggplot(plotting_df_pearson_cocl2[sample(1:nrow(plotting_df_pearson_cocl2), 10000000),], aes(x = Treatment, y = Pearson, fill = Grouping)) + geom_violin() + geom_boxplot(width = 0.1, outlier.shape = NA) +
  scale_fill_manual(values=c("#FF0000", "#D3D3D3", "#0000FF"))
dev.off()

# Save outputs
save(pearson_ttest_cocl2_firstvsrand, pearson_ttest_cocl2_secondvsfirst, pearson_ttest_cocl2_secondvsrand, pearson_ttest_cocl2_randvsrand, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/cocl2_pearson_values.RData')
rm(pearson_ttest_cocl2_firstvsrand, pearson_ttest_cocl2_secondvsfirst, pearson_ttest_cocl2_secondvsrand, pearson_ttest_cocl2_randvsrand)

save(plotting_df_pearson_cocl2, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/cocl2_pearson_plotting_df.RData')
rm(plotting_df_pearson_cocl2)
```

# Statistical analysis and plotting of pearson metrics - dabtram
```{r}
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/dabtram_pearson_results.RData') # Load data

pearson_ttest_dabtram_firstvsrand <- t.test(dabtram_first_pearson_filt, dabtram_first_pearson_filt_rand,  paired = F)
pearson_ttest_dabtram_secondvsrand <- t.test(dabtram_second_pearson_filt, dabtram_second_pearson_filt_rand,  paired = F)
pearson_ttest_dabtram_secondvsfirst <- t.test(dabtram_second_pearson_filt, dabtram_first_pearson_filt,  paired = F)
pearson_ttest_dabtram_randvsrand <- t.test(dabtram_second_pearson_filt_rand, dabtram_first_pearson_filt_rand,  paired = F)

rm(dabtram_first_pearson, dabtram_first_pearson_rand, dabtram_first_subset, dabtram_first_subset_rand, dabtram_second_pearson, dabtram_second_pearson_rand, dabtram_second_subset, dabtram_second_subset_rand)

plotting_df_pearson_dabtram <- data.frame(Grouping = c(rep('first',length(dabtram_first_pearson_filt)), rep('random',length(dabtram_first_pearson_filt)), rep('second', length(dabtram_second_pearson_filt)), rep('random', length(dabtram_second_pearson_filt))),
                          Pearson = c(dabtram_first_pearson_filt, dabtram_first_pearson_filt_rand, dabtram_second_pearson_filt, dabtram_second_pearson_filt_rand),
                          Treatment = c(rep('dabtram first',length(dabtram_first_pearson_filt)), rep('dabtram first rand', length(dabtram_first_pearson_filt_rand)),rep('dabtram second',length(dabtram_second_pearson_filt)),rep('dabtram second rand',length(dabtram_second_pearson_filt_rand))))
colnames(plotting_df_pearson_dabtram) <- c('Grouping','Pearson','Treatment')

rm(dabtram_first_pearson_filt, dabtram_first_pearson_filt_rand, dabtram_second_pearson_filt, dabtram_second_pearson_filt_rand)
gc()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/dabtram_pearson_plot_subsampled.pdf')
set.seed(1)
ggplot(plotting_df_pearson_dabtram[sample(1:nrow(plotting_df_pearson_dabtram), 10000000),], aes(x = Treatment, y = Pearson, fill = Grouping)) + geom_violin() + geom_boxplot(width = 0.1, outlier.shape = NA) +
  scale_fill_manual(values=c("#FF0000", "#D3D3D3", "#0000FF"))
dev.off()

# Save outputs
save(pearson_ttest_dabtram_firstvsrand, pearson_ttest_dabtram_secondvsfirst, pearson_ttest_dabtram_secondvsrand,pearson_ttest_dabtram_randvsrand, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/dabtram_pearson_values.RData')
rm(pearson_ttest_dabtram_firstvsrand, pearson_ttest_dabtram_secondvsfirst, pearson_ttest_dabtram_secondvsrand, pearson_ttest_dabtram_randvsrand)

save(plotting_df_pearson_dabtram, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/dabtram_pearson_plotting_df.RData')
rm(plotting_df_pearson_dabtram)
```

# Statistical analysis and plotting of pearson metrics - cis
```{r}
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/cis_pearson_results.RData') # Load data

pearson_ttest_cis_firstvsrand <- t.test(cis_first_pearson_filt, cis_first_pearson_filt_rand,  paired = F)
pearson_ttest_cis_secondvsrand <- t.test(cis_second_pearson_filt, cis_second_pearson_filt_rand,  paired = F)
pearson_ttest_cis_secondvsfirst <- t.test(cis_second_pearson_filt, cis_first_pearson_filt,  paired = F)
pearson_ttest_cis_randvsrand <- t.test(cis_second_pearson_filt_rand, cis_first_pearson_filt_rand,  paired = F)

rm(cis_first_pearson, cis_first_pearson_rand, cis_first_subset, cis_first_subset_rand, cis_second_pearson, cis_second_pearson_rand, cis_second_subset, cis_second_subset_rand)

plotting_df_pearson_cis <- data.frame(Grouping = c(rep('first',length(cis_first_pearson_filt)), rep('random',length(cis_first_pearson_filt)), rep('second', length(cis_second_pearson_filt)), rep('random', length(cis_second_pearson_filt))),
                          Pearson = c(cis_first_pearson_filt, cis_first_pearson_filt_rand, cis_second_pearson_filt, cis_second_pearson_filt_rand),
                          Treatment = c(rep('cis first',length(cis_first_pearson_filt)), rep('cis first rand', length(cis_first_pearson_filt_rand)),rep('cis second',length(cis_second_pearson_filt)),rep('cis second rand',length(cis_second_pearson_filt_rand))))
colnames(plotting_df_pearson_cis) <- c('Grouping','Pearson','Treatment')

rm(cis_first_pearson_filt, cis_first_pearson_filt_rand, cis_second_pearson_filt, cis_second_pearson_filt_rand)
gc()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/cis_pearson_plot_subsampled.pdf')
set.seed(1)
ggplot(plotting_df_pearson_cis[sample(1:nrow(plotting_df_pearson_cis), 10000000),], aes(x = Treatment, y = Pearson, fill = Grouping)) + geom_violin() + geom_boxplot(width = 0.1, outlier.shape = NA) +
  scale_fill_manual(values=c("#FF0000", "#D3D3D3", "#0000FF"))
dev.off()

# Save outputs
save(pearson_ttest_cis_firstvsrand, pearson_ttest_cis_secondvsfirst, pearson_ttest_cis_secondvsrand, pearson_ttest_cis_randvsrand, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/cis_pearson_values.RData')
rm(pearson_ttest_cis_firstvsrand, pearson_ttest_cis_secondvsfirst, pearson_ttest_cis_secondvsrand, pearson_ttest_cis_randvsrand)

save(plotting_df_pearson_cis, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/cis_pearson_plotting_df.RData')
rm(plotting_df_pearson_cis)
```

# Load in the ttest data and compile into excel sheet
```{r}
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/cocl2_pearson_values.RData')
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/dabtram_pearson_values.RData')
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/cis_pearson_values.RData')

comparisons <-  c('dabtram_firstvsrand', 'dabtram_secondvsrand', 'dabtram_randvsrand', 'dabtram_secondvsfirst',
                  'cocl2_firstvsrand', 'cocl2_secondvsrand', 'cocl2_randvsrand', 'cocl2_secondvsfirst',
                  'cis_firstvsrand', 'cis_secondvsrand', 'cis_randvsrand', 'cis_secondvsfirst')

t_statistic <- c(pearson_ttest_dabtram_firstvsrand$statistic, pearson_ttest_dabtram_secondvsrand$statistic, pearson_ttest_dabtram_randvsrand$statistic, pearson_ttest_dabtram_secondvsfirst$statistic,
                 pearson_ttest_cocl2_firstvsrand$statistic, pearson_ttest_cocl2_secondvsrand$statistic,pearson_ttest_cocl2_randvsrand$statistic, pearson_ttest_cocl2_secondvsfirst$statistic,
                 pearson_ttest_cis_firstvsrand$statistic, pearson_ttest_cis_secondvsrand$statistic, pearson_ttest_cis_randvsrand$statistic, pearson_ttest_cis_secondvsfirst$statistic)

t_pval <- c(pearson_ttest_dabtram_firstvsrand$p.value, pearson_ttest_dabtram_secondvsrand$p.value, pearson_ttest_dabtram_randvsrand$p.value, pearson_ttest_dabtram_secondvsfirst$p.value,
            pearson_ttest_cocl2_firstvsrand$p.value, pearson_ttest_cocl2_secondvsrand$p.value, pearson_ttest_cocl2_randvsrand$p.value, pearson_ttest_cocl2_secondvsfirst$p.value,
            pearson_ttest_cis_firstvsrand$p.value, pearson_ttest_cis_secondvsrand$p.value, pearson_ttest_cis_randvsrand$p.value, pearson_ttest_cis_secondvsfirst$p.value)

ttest_df <- data.frame('Comparisons' = comparisons, 'T test statistic' = t_statistic, 'p value' = t_pval)

write.xlsx(ttest_df, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Condition_Clustering/pearson_ttest_statistics.xlsx')
```



