---
title: "UMAPs_continued_treatment"
output: html_document
---

#Set working directory to appropriate folder for inputs and outputs on Google Drive
```{r, setup, include=FALSE}
#knitr::opts_knit$set(root.dir = '/Volumes/GoogleDrive/My Drive/Fasse_Shared/AJF_Drive_copy/Experiments/AJF009') # for aria's computer
knitr::opts_knit$set(root.dir = '/Users/dylanschaff/Library/CloudStorage/GoogleDrive-dyschaff@sydshafferlab.com/.shortcut-targets-by-id/1zSqx3IzXMwt6clUjwyqmlOf4G1K53lvy/Fasse_Shared/AJF_Drive_copy/Experiments/AJF009') # for dylan's computer

#2022_01_14_analysis_scripts/2022_05_27_analysis/Lineage_expression/ is additional path for outputs

```

#Initialize
```{r include = FALSE}
rm(list = ls())
library(dplyr)
library(Seurat)
library(ggplot2)
library(RColorBrewer)
library(ggpubr)
library(pheatmap)
library(viridis)
library(xlsx)
library(escape)
library(dittoSeq)
library(tidyverse)

`%nin%` = Negate(`%in%`)
```

# Load data
```{r}
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Assign_dominant_barcodes/all_data_final_lineages.RData')
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/second_timepoint_merged.RData')
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Filtering_cDNA/resistant_lineage_lists.RData')

```

# Markers within each first drug object to find subgroups (ie analogous to NGFR/EGFR)
```{r include = FALSE}
#load('2022_01_14_analysis_scripts/2022_05_27_analysis/Lineage_expression/all_data_markers.RData')
cis_markers <- FindAllMarkers(cis, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
cocl2_markers <- FindAllMarkers(cocl2, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
dabtram_markers <- FindAllMarkers(dabtram, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)

all_data.markers <- FindAllMarkers(all_data, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25) 
save(all_data.markers, cis_markers, cocl2_markers, dabtram_markers, file = 'all_data_markers.RData')
```

#makedabtram continued, force 2 clusters in umap, plot vs ngfr egfr, find markers of these 2
```{r}
Idents(all_data) <- all_data$OG_condition # Change the idents to the OG condition for subsetting to dabtram
dabtram_continued <- subset(all_data, idents = c('dabtram', 'dabtramtodabtram')) # Subset down to the dabtram object
dabtram_continued <- NormalizeData(dabtram_continued)
dabtram_continued <- FindVariableFeatures(dabtram_continued, selection.method = 'vst', nFeatures = 20000)
dabtram_continued <- ScaleData(dabtram_continued)
dabtram_continued <- RunPCA(dabtram_continued)
dabtram_continued <- FindNeighbors(dabtram_continued, dims = 1:15)
dabtram_continued <- FindClusters(dabtram_continued, resolution = 0.015)
dabtram_continued <- RunUMAP(dabtram_continued, dims = 1:15)

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Continued_Treatment/dabtram_continued_umaps.pdf')
DimPlot(dabtram_continued, group.by = 'OG_condition', pt.size = 2, cols = c('dabtram' = '#623594','dabtramtodabtram' = '#561E59'))
DimPlot(dabtram_continued, pt.size = 2)
FeaturePlot(dabtram_continued, features = c('NGFR'), pt.size = 2)+
  scale_colour_gradientn(colors = rev(brewer.pal(n = 11, name = 'RdBu')))
FeaturePlot(dabtram_continued, features = c('EGFR'), pt.size = 2)+
  scale_colour_gradientn(colors = rev(brewer.pal(n = 11, name = 'RdBu')))
dev.off()

```

#Assign cluster assignments per lineage, find average score per lineage - make plots in order
```{r}
#average cell assignments per lineage in dabtram_maintained

#get lineage and cluster data from seurat object, switch cluster identifiers from 0,1 to -1,1 (egfr, ngfr)
clusters_per_lin <- data.frame (Cluster = as.numeric(as.character(dabtram_continued$seurat_clusters)), Lineage = dabtram_continued$Lineage, condition = dabtram_continued$OG_condition)
clusters_per_lin$Cluster[clusters_per_lin$Cluster == 0] <- -1
clusters_per_lin_list <- list()

# Need to get percent values of EGFR for the lineage after the first treatment
for (i in fivecell_cDNA$DabTram){
  currentlin <- filter(clusters_per_lin, clusters_per_lin$Lineage == i & clusters_per_lin$condition == 'dabtram')
  Var1 <- c(-1,1)
  Freq <- c(sum(filter(clusters_per_lin, clusters_per_lin$Lineage == i & clusters_per_lin$condition == 'dabtram')$Cluster == -1), # EGFR
  sum(filter(clusters_per_lin, clusters_per_lin$Lineage == i & clusters_per_lin$condition == 'dabtram')$Cluster == 1))
  clusters_per_lin_list[[i]] <- data.frame('Var1' = Var1, 'Freq' = Freq)
  clusters_per_lin_list[[i]]$Score <- weighted.mean(as.numeric(as.character(clusters_per_lin_list[[i]]$Var1)), clusters_per_lin_list[[i]]$Freq)
}

# Build a dataframe for plotting based on % EGFR or NGFR per lineage after first treatment
clusters_per_lin_df <- data.frame(matrix(ncol = 5, nrow = 0))
colnames(clusters_per_lin_df) <- c('Lineage', 'Percent_cells', 'Num_cells', 'Score')
for (i in names(clusters_per_lin_list)){
    clusters_per_lin_df <- rbind(clusters_per_lin_df, data.frame('Lineage' = i, 'Percent_cells' = clusters_per_lin_list[[i]]$Freq[clusters_per_lin_list[[i]]$Var1 == 1]/sum(clusters_per_lin_list[[i]]$Freq), 'Num_cells' = sum(clusters_per_lin_list[[i]]$Freq[clusters_per_lin_list[[i]]$Var1 == 1]), 'Score' = clusters_per_lin_list[[i]]$Score[1], 'Cluster' = 'NGFR')) # Add NGFR row
  clusters_per_lin_df <- rbind(clusters_per_lin_df, data.frame('Lineage' = i, 'Percent_cells' = clusters_per_lin_list[[i]]$Freq[clusters_per_lin_list[[i]]$Var1 == -1]/sum(clusters_per_lin_list[[i]]$Freq), 'Num_cells' = sum(clusters_per_lin_list[[i]]$Freq[clusters_per_lin_list[[i]]$Var1 == -1]), 'Score' = clusters_per_lin_list[[i]]$Score[1], 'Cluster' = 'EGFR')) # Add EGFR row
}

# Reorder so that EGFR dominant lineages are plot first
clusters_per_lin_df <- clusters_per_lin_df[with(clusters_per_lin_df, order(-Score,Num_cells )),]
clusters_per_lin_df$Lineage <- factor(clusters_per_lin_df$Lineage, levels = rev(unique(clusters_per_lin_df$Lineage)))

# make list object for after second treatment
clusters_per_lin_list_sec <- list()

# Need to get percent values of EGFR for the lineage after the second treatment
for (i in fivecell_cDNA$DabTram){
  currentlin <- filter(clusters_per_lin, clusters_per_lin$Lineage == i & clusters_per_lin$condition == 'dabtramtodabtram')
  Var1 <- c(-1,1)
  Freq <- c(sum(filter(clusters_per_lin, clusters_per_lin$Lineage == i & clusters_per_lin$condition == 'dabtramtodabtram')$Cluster == -1), # EGFR
  sum(filter(clusters_per_lin, clusters_per_lin$Lineage == i & clusters_per_lin$condition == 'dabtramtodabtram')$Cluster == 1))
  clusters_per_lin_list_sec[[i]] <- data.frame('Var1' = Var1, 'Freq' = Freq)
  clusters_per_lin_list_sec[[i]]$Score <- weighted.mean(as.numeric(as.character(clusters_per_lin_list_sec[[i]]$Var1)), clusters_per_lin_list_sec[[i]]$Freq)
}

# Build a dataframe for plotting based on % EGFR or NGFR per lineage after second treatment
clusters_per_lin_df_sec <- data.frame(matrix(ncol = 5, nrow = 0))
colnames(clusters_per_lin_df_sec) <- c('Lineage', 'Percent_cells', 'Num_cells', 'Score', 'Cluster')
for (i in names(clusters_per_lin_list)){

  if (sum(clusters_per_lin_list_sec[[i]]$Freq) < 5){
    clusters_per_lin_df_sec <- rbind(clusters_per_lin_df_sec, data.frame('Lineage' = i, 'Percent_cells' = 1, 'Num_cells' = 0, 'Score' = 0, 'Cluster' = 'Died')) # Add Lineage died row
    clusters_per_lin_df_sec <- rbind(clusters_per_lin_df_sec, data.frame('Lineage' = i, 'Percent_cells' = 0, 'Num_cells' = 0, 'Score' = 0, 'Cluster' = 'NGFR')) # Add NGFR row
    clusters_per_lin_df_sec <- rbind(clusters_per_lin_df_sec, data.frame('Lineage' = i, 'Percent_cells' = 0, 'Num_cells' = 0, 'Score' = 0, 'Cluster' = 'EGFR')) # Add EGFR row
  }else{ # Actually calculate percentages since the lineage survived/is more than 5 cells
      clusters_per_lin_df_sec <- rbind(clusters_per_lin_df_sec, data.frame('Lineage' = i, 'Percent_cells' = 0, 'Num_cells' = 0, 'Score' = clusters_per_lin_list_sec[[i]]$Score[1], 'Cluster' = 'Died')) # Add Lineage died row
      clusters_per_lin_df_sec <- rbind(clusters_per_lin_df_sec, data.frame('Lineage' = i, 'Percent_cells' = clusters_per_lin_list_sec[[i]]$Freq[clusters_per_lin_list_sec[[i]]$Var1 == 1]/sum(clusters_per_lin_list_sec[[i]]$Freq), 'Num_cells' = sum(clusters_per_lin_list_sec[[i]]$Freq[clusters_per_lin_list_sec[[i]]$Var1 == 1]), 'Score' = clusters_per_lin_list_sec[[i]]$Score[1], 'Cluster' = 'NGFR')) # Add NGFR row
      clusters_per_lin_df_sec <- rbind(clusters_per_lin_df_sec, data.frame('Lineage' = i, 'Percent_cells' = clusters_per_lin_list_sec[[i]]$Freq[clusters_per_lin_list_sec[[i]]$Var1 == -1]/sum(clusters_per_lin_list_sec[[i]]$Freq), 'Num_cells' = sum(clusters_per_lin_list_sec[[i]]$Freq[clusters_per_lin_list_sec[[i]]$Var1 == -1]), 'Score' = clusters_per_lin_list_sec[[i]]$Score[1], 'Cluster' = 'EGFR')) # Add EGFR row
    }
}

# Reorder so that EGFR dominant lineages are plot first
clusters_per_lin_df_sec$Lineage <- factor(clusters_per_lin_df_sec$Lineage, levels = rev(unique(clusters_per_lin_df$Lineage)))

# Plot
p1 <- ggplot(clusters_per_lin_df, aes(y = Percent_cells, x = Lineage, fill = Cluster)) + geom_bar(stat = 'identity', position = position_fill(reverse = T), color = '#D3D3D3') + scale_fill_manual(values = c("#000000","#FFFFFF")) + theme_classic() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
p2 <- ggplot(clusters_per_lin_df_sec, aes(y = Percent_cells, x = Lineage, fill = Cluster)) + geom_bar(stat = 'identity', position = position_fill(reverse = T), color = '#D3D3D3') + scale_fill_manual(values = c("#FF0000","#000000", '#FFFFFF')) + theme_classic() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Continued_Treatment/stacked_bar_EGFR_NGFR_Died.pdf')
ggarrange(p1,p2, nrow = 2)
dev.off()
```

# Plot the number of cells per lineage in second drug for lineages that survived in DabTram
```{r}
# Get the number of cells in the DabTram resistant lineages in the conditions that got DabTram first
dabtramtodabtram_dt_resist_lins <- list()
dabtramtococl2_dt_resist_lins <- list()
dabtramtocis_dt_resist_lins <- list()

for (i in fivecell_cDNA$DabTram){
  dabtramtodabtram_dt_resist_lins[[i]] <- all_data$Lineage[all_data$Lineage == i & all_data$OG_condition == 'dabtramtodabtram']
  dabtramtococl2_dt_resist_lins[[i]] <- all_data$Lineage[all_data$Lineage == i & all_data$OG_condition == 'dabtramtococl2']
  dabtramtocis_dt_resist_lins[[i]] <- all_data$Lineage[all_data$Lineage == i & all_data$OG_condition == 'dabtramtocis']
}
scaleFUN <- function(x) sprintf("%.2f", x)

# convert list to dataframe
dabtramtodabtram_dt_resist_lins_df <- data.frame(num_cells = lengths(dabtramtodabtram_dt_resist_lins))
dabtramtodabtram_dt_resist_lins_df$Lineage = rownames(dabtramtodabtram_dt_resist_lins_df)
dabtramtodabtram_dt_resist_lins_df$Lineage <- factor(dabtramtodabtram_dt_resist_lins_df$Lineage, levels = rev(unique(clusters_per_lin_df$Lineage)))

dabtramtococl2_dt_resist_lins_df <- data.frame(num_cells = lengths(dabtramtococl2_dt_resist_lins))
dabtramtococl2_dt_resist_lins_df$Lineage = rownames(dabtramtococl2_dt_resist_lins_df)
dabtramtococl2_dt_resist_lins_df$Lineage <- factor(dabtramtococl2_dt_resist_lins_df$Lineage, levels = rev(unique(clusters_per_lin_df$Lineage)))

dabtramtocis_dt_resist_lins_df <- data.frame(num_cells = lengths(dabtramtocis_dt_resist_lins))
dabtramtocis_dt_resist_lins_df$Lineage = rownames(dabtramtocis_dt_resist_lins_df)
dabtramtocis_dt_resist_lins_df$Lineage <- factor(dabtramtocis_dt_resist_lins_df$Lineage, levels = rev(unique(clusters_per_lin_df$Lineage)))

# Plot 
p3 <- ggplot(dabtramtodabtram_dt_resist_lins_df, aes(y = log(num_cells+1), x = Lineage)) + geom_col(fill = '#561E59') + theme_classic() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + labs(title = 'DabTram to DabTram') + scale_y_continuous(labels = scaleFUN)

p4 <- ggplot(dabtramtococl2_dt_resist_lins_df, aes(y = log(num_cells+1), x = Lineage)) + geom_col(fill = '#A2248E') + theme_classic() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + labs(title = 'DabTram to CoCl2') + scale_y_continuous(labels = scaleFUN)

p5 <- ggplot(dabtramtocis_dt_resist_lins_df, aes(y = log(num_cells+1), x = Lineage)) + geom_col(fill = '#9D85BE') + theme_classic() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + labs(title = 'DabTram to Cis') + scale_y_continuous(labels = scaleFUN)

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Continued_Treatment/stacked_bar_EGFR_NGFR_Died_w_other_second_drugs.pdf', height = 14)
ggarrange(p1+ theme(legend.position = 'bottom'),p2+ theme(legend.position = 'bottom'),p3,p4,p5, nrow = 5)
dev.off()


```

#make cis continued
```{r}
Idents(all_data) <- all_data$OG_condition # Change the idents to the OG condition for subsetting to cis
cis_continued <- subset(all_data, idents = c('cis', 'cistocis')) # Subset down to the cis object
cis_continued <- NormalizeData(cis_continued)
cis_continued <- FindVariableFeatures(cis_continued, selection.method = 'vst', nFeatures = 20000)
cis_continued <- ScaleData(cis_continued)
cis_continued <- RunPCA(cis_continued)
cis_continued <- FindNeighbors(cis_continued, dims = 1:15)
cis_continued <- FindClusters(cis_continued, resolution = 0.5)
cis_continued <- RunUMAP(cis_continued, dims = 1:15)

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Continued_Treatment/cis_continued_umaps.pdf')
DimPlot(cis_continued, group.by = 'OG_condition', pt.size = 2, cols = c('cis' = '#c96d29','cistocis' = '#fbd08c'))
dev.off()

```

#make cocl2 continued
```{r}
Idents(all_data) <- all_data$OG_condition # Change the idents to the OG condition for subsetting to cocl2
cocl2_continued <- subset(all_data, idents = c('cocl2', 'cocl2tococl2')) # Subset down to the cocl2 object
cocl2_continued <- NormalizeData(cocl2_continued)
cocl2_continued <- FindVariableFeatures(cocl2_continued, selection.method = 'vst', nFeatures = 20000)
cocl2_continued <- ScaleData(cocl2_continued)
cocl2_continued <- RunPCA(cocl2_continued)
cocl2_continued <- FindNeighbors(cocl2_continued, dims = 1:15)
cocl2_continued <- FindClusters(cocl2_continued, resolution = 0.5)
cocl2_continued <- RunUMAP(cocl2_continued, dims = 1:15)

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Continued_Treatment/cocl2_continued_umaps.pdf')
DimPlot(cocl2_continued, group.by = 'OG_condition', pt.size = 2, cols = c('cocl2' = '#0f8241','cocl2tococl2' = '#6abd45'))
dev.off()

```


# do ssGSEA on EGFR-high, NGFR-high, and mixed clones
```{r}

Idents(all_data) <- all_data$OG_condition
dabtram <- subset(all_data, idents = 'dabtram')

# Get just the cells of interest from the lineages with more than 5 cells and normalize
Idents(all_data) <- all_data$OG_condition # Change the idents to the OG condition for subsetting to cocl2
dabtram <- subset(all_data, idents = c('dabtram'))
Idents(dabtram) <- dabtram$Lineage
dt_sub <- subset(dabtram, idents = fivecell_cDNA$DabTram)
dt_sub <- NormalizeData(dt_sub)
dt_sub <- FindVariableFeatures(dt_sub, selection.method = 'vst', nFeatures = 20000)
dt_sub <- ScaleData(dt_sub)
dt_sub <- RunPCA(dt_sub)
dt_sub <- FindNeighbors(dt_sub, dims = 1:15)
dt_sub <- FindClusters(dt_sub, resolution = 0.5)
dt_sub <- RunUMAP(dt_sub, dims = 1:15)

# Load in data from: doi: 10.1016/j.ccell.2018.03.017 and format as lists
Tsoi_data <- read.xlsx('2022_01_14_analysis_scripts/2022_05_27_analysis/Continued_Treatment/NIHMS955175-supplement-4.xlsx',1, header = T)
colnames(Tsoi_data) <- Tsoi_data[1,]
Tsoi_data <- Tsoi_data[-1,-3]
Tsoi_list <- Tsoi_data %>% group_by(Signature) %>% summarize(Gene = list(Gene)) %>% deframe()

# Add metadata for EGFR high, NGFR high, and mixed clones
cluster_meta <- list()
for (i in fivecell_cDNA$DabTram){
  if (clusters_per_lin_df$Score[clusters_per_lin_df$Lineage == i & clusters_per_lin_df$Cluster == 'NGFR'] == 1){
    cluster_meta[[i]] <- 'NGFR-high'
  }else if (clusters_per_lin_df$Score[clusters_per_lin_df$Lineage == i & clusters_per_lin_df$Cluster == 'EGFR'] == -1){
    cluster_meta[[i]] <- 'EGFR-high'
  }else if (clusters_per_lin_df$Score[clusters_per_lin_df$Lineage == i & clusters_per_lin_df$Cluster == 'NGFR'] != 1 & clusters_per_lin_df$Score[clusters_per_lin_df$Lineage == i & clusters_per_lin_df$Cluster == 'EGFR'] != -1 ){
    cluster_meta[[i]] <- 'Mixed'
  }
}
cluster_meta <- unlist(cluster_meta)
dt_sub$cluster <- cluster_meta[dt_sub$Lineage]

# Perform enrichment
enriched <- enrichIt(obj = dt_sub,
                     gene.sets = Tsoi_list,
                     cores = 4,
                     min.size = 5,
                     method = 'UCell')
dt_sub <- AddMetaData(dt_sub, enriched)

# Plot the data
colors <- colorRampPalette(c("#0D0887FF","#7E03A8FF","#CC4678FF","#F89441FF","#F0F921FF"))
pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Continued_Treatment/GSEA_and_scoring.pdf')
dittoHeatmap(dt_sub, genes = NULL, metas = names(enriched), 
             annot.by = "cluster", 
             fontsize = 7, 
             cluster_cols = TRUE,
             heatmap.colors = colors(50))

multi_dittoPlot(dt_sub, vars = names(enriched), 
                group.by = "cluster", plots = c("jitter", "vlnplot", "boxplot"), 
                ylab = "Enrichment Scores", 
                theme = theme_classic() + theme(plot.title = element_text(size = 10)))

multi_dittoPlot(dt_sub, vars = c('Melanocytic','Neural.crest.like','Transitory','Undifferentiated'), 
                group.by = "cluster", plots = c("jitter", "vlnplot", "boxplot"), 
                ylab = "Enrichment Scores", 
                theme = theme_classic() + theme(plot.title = element_text(size = 10)), ncol = 2)

multi_dittoPlot(dt_sub, vars = c('Melanocytic'), 
                group.by = "cluster", plots = c("jitter", "vlnplot", "boxplot"), 
                ylab = "Enrichment Scores", 
                theme = theme_classic() + theme(plot.title = element_text(size = 10)), ncol = 1, nrow = 1)

multi_dittoPlot(dt_sub, vars = c('Neural.crest.like'), 
                group.by = "cluster", plots = c("jitter", "vlnplot", "boxplot"), 
                ylab = "Enrichment Scores", 
                theme = theme_classic() + theme(plot.title = element_text(size = 10)), ncol = 1, nrow = 1)

multi_dittoPlot(dt_sub, vars = c('Transitory'), 
                group.by = "cluster", plots = c("jitter", "vlnplot", "boxplot"), 
                ylab = "Enrichment Scores", 
                theme = theme_classic() + theme(plot.title = element_text(size = 10)), ncol = 1, nrow = 1)

multi_dittoPlot(dt_sub, vars = c('Undifferentiated'), 
                group.by = "cluster", plots = c("jitter", "vlnplot", "boxplot"), 
                ylab = "Enrichment Scores", 
                theme = theme_classic() + theme(plot.title = element_text(size = 10)), ncol = 1, nrow = 1)

## Seurat object example
Idents(dt_sub) <- dt_sub$cluster
ES2 <- data.frame(dt_sub[[]], Idents(dt_sub))
colnames(ES2)[ncol(ES2)] <- "cluster"
dev.off()

output <- getSignificance(ES2, # https://rdrr.io/github/ncborcherding/escape/man/getSignificance.html
                          group = "cluster", 
                          gene.sets = names(enriched),
                          fit = "ANOVA")

write.xlsx(output, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Continued_Treatment/GSEA_and_scoring.xlsx')
```