---
title: "2022_06_14_test_barcode_assignment of cDNA into GEX"
output: html_notebook
---

#Set working directory to appropriate folder for inputs and outputs on Google Drive
```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '/Volumes/GoogleDrive/My Drive/Fasse_Shared/AJF_Drive_copy/Experiments/AJF009') # for aria's computer
#knitr::opts_knit$set(root.dir = '/Volumes/GoogleDrive/.shortcut-targets-by-id/1zSqx3IzXMwt6clUjwyqmlOf4G1K53lvy/Fasse_Shared/AJF_Drive_copy/Experiments/AJF009') # for dylan's computer

#2022_01_14_analysis_scripts/2022_05_27_analysis/Test_barcode_assignment/ is additional path for outputs
```

# Initialize ----
```{r include = FALSE}
rm(list = ls())
library(dplyr)
library(Seurat)
library(ggplot2)
library(RColorBrewer)
library(kit)
```

# Load in the merged dataset for all data
```{r include = FALSE}

load('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/all_data_merged.RData')
reference <- read.delim('2022_05_19_Barcode_outputs/CellRanger_inputs/FeatureReference_filtered.csv')

```

# Build counts object
```{r include = FALSE}

counts <- GetAssayData(all_data, assay = 'lineage')
num_lin_orig <- nrow(counts)

```

# Remove lineages with only one count across all cells
```{r}

counts_filt <- counts[which(rowSums(counts) > 1),] # Only care about lineages that have greater than one total count
num_lin_filt <- nrow(counts_filt)
percent_lin_filt <- num_lin_filt/num_lin_orig*100

df_counts <- as.data.frame(counts_filt)

```

# Find number of barcodes per cell
```{r}

barcodes_per_cell <- apply(counts_filt,2, function(x) sum(x>0))
barcodes_per_cell_table <- table(barcodes_per_cell)
barcodes_per_cell_table

```

# Plotting cells per lineage for each condition
```{r}

plot_df_list <- list() 
for (k in unique(all_data$OG_condition)){
  print(k)
  plot_df <- data.frame()
  for (i in 1:50){ # 1:20
    temp_fam_list <- list()
    print(i)
    count <- 1
    for (j in grep(k,colnames(counts_filt))){
      temp_fam_list[[count]] <- which(counts_filt[,j] > i)
      count <- count+1
    }
    table <- table(lengths(temp_fam_list))
    temp <- data.frame(zero = as.numeric(table[1]), one = as.numeric(table[2]), two_or_more = length(temp_fam_list) - as.numeric(table[1]) - as.numeric(table[2]))
    plot_df <- rbind(plot_df,temp)
  }
  plot_df_list[[k]] <- plot_df
}

```

# Build plot list of count cutoffs which give # of cells with either no, 1, many barcodes and plot to pdf
```{r}
plot_df_list2 <- list()
for (i in names(plot_df_list)){
  plot_df_list2[[i]] <- data.frame(
    count_filt = rep(1:50,3),
    num_cells = unlist(plot_df_list[[i]]),
    barcode_num = c(rep('zero',50),rep('one',50), rep('multiple',50))
  )
}

# Write the plots to a PDF
pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Test_barcode_assignment/threshold_sweep.pdf')
for (i in names(plot_df_list2)){
  print(ggplot(data = plot_df_list2[[i]], aes(x = count_filt, y = num_cells, group = barcode_num, color = barcode_num)) + geom_point()+geom_line() + labs(title = i))
}
dev.off()
```

# Finding best ways to threshold
```{r}
cutoffs <- data.frame()
for(i in names(plot_df_list2)){
  zero <- plot_df_list2[[i]][plot_df_list2[[i]]$barcode_num == 'zero',]
  one <- plot_df_list2[[i]][plot_df_list2[[i]]$barcode_num == 'one',]
  multiple <- plot_df_list2[[i]][plot_df_list2[[i]]$barcode_num == 'multiple',]
  cutoffs <- rbind(cutoffs, data.frame(Max_single = which.max(one$num_cells), Max_ratio = which.max(one$num_cells/multiple$num_cells), Max_difference = which.max(one$num_cells - multiple$num_cells)))
}
rownames(cutoffs) <- names(plot_df_list2)

# Export the cutoffs so that it can be loaded in for final barcode assignment script
save(cutoffs, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Test_barcode_assignment/lineage_count_cutoffs.RData')

```

# Filter based on reads cutoff that results in max # of cells with single barcode assignment
```{r}
# filter based on the Max_single
filter_max_single <- cutoffs$Max_single
names(filter_max_single) <- names(plot_df_list)

# filter based on decided threshold
fam_max_single <- list()
for (k in names(filter_max_single)){
  for (i in grep(k,colnames(df_counts))){
    fam_max_single[[i]] <- rownames(df_counts)[which(df_counts[,i] > filter_max_single[k])]
  }
}
# See how many cells still have reads from how many barcodes
table_fam_max_single <- table(lengths(fam_max_single))
```

# Filter based on max difference in # cells assigned one and multiple barcodes
```{r}
# filter based on the Max_difference
filter_max_difference <- cutoffs$Max_difference
names(filter_max_difference) <- names(plot_df_list)

# filter based on decided threshold
fam_max_difference <- list()
for (k in names(filter_max_difference)){
  for (i in grep(k,colnames(df_counts))){
    fam_max_difference[[i]] <- rownames(df_counts)[which(df_counts[,i] > filter_max_difference[k])]
  }
}
# See how many cells still have reads from how many barcodes
table_fam_max_difference <- table(lengths(fam_max_difference))
```

#write to csv
```{r}
write.csv(table_fam_max_single, file = "2022_01_14_analysis_scripts/2022_05_27_analysis/Test_barcode_assignment/table_fam_max_single.csv")
write.csv(table_fam_max_difference, file = "2022_01_14_analysis_scripts/2022_05_27_analysis/Test_barcode_assignment/table_fam_max_difference.csv")
```

# Build a boolean of the cells that still have multiple barcodes - max_single
```{r}
boolean_multi_lin_single <- lengths(fam_max_single)>1
```

# Assign dominant barcode if one is highly more expressed, write to csv
```{r}
fixed_multi_single <- list()
for (i in (1:ncol(df_counts))){ 
  if ( boolean_multi_lin_single[i] == T) {
    if(df_counts[topn(as.numeric(df_counts[,i]),2),i][1] >= 3*df_counts[topn(as.numeric(df_counts[,i]),2),i][2]){
      fixed_multi_single[[i]] <- rownames(df_counts)[topn(as.numeric(df_counts[,i]),2)][1]
    }else{
      fixed_multi_single[[i]] <- "Still multiple"
    }
  } else{ fixed_multi_single[[i]] <- "Single"
  }
}

# Build a boolean of the cells that still have multiple barcodes - max_difference
boolean_multi_lin_difference <- lengths(fam_max_difference)>1

# Assign dominant barcode if the number of counts in the highest expressed barcodes is >triple that of second highest barcode
fixed_multi_difference <- list()
for (i in (1:ncol(df_counts))){ 
  if ( boolean_multi_lin_difference[i] == T) {
    if(df_counts[topn(as.numeric(df_counts[,i]),2),i][1] >= 3*df_counts[topn(as.numeric(df_counts[,i]),2),i][2]){
      fixed_multi_difference[[i]] <- rownames(df_counts)[topn(as.numeric(df_counts[,i]),2)][1]
    }else{
      fixed_multi_difference[[i]] <- "Still multiple"
    }
  } else{ fixed_multi_difference[[i]] <- "Single"
  }
}

# Replace the values in fam that had 2+ barcodes with with either the dominant barcode if found or say that its still multiple - max single
fam_multi_collapse_single <- fam_max_single
fam_multi_collapse_single[boolean_multi_lin_single] <- fixed_multi_single[boolean_multi_lin_single]

# Replace the values in fam that had 2+ barcodes with with either the dominant barcode if found or say that its still multiple - max difference
fam_multi_collapse_difference <- fam_max_difference
fam_multi_collapse_difference[boolean_multi_lin_difference] <- fixed_multi_difference[boolean_multi_lin_difference]

# Give cells without a barcode the label 'No barcode'
fam_multi_collapse_single[lengths(fam_multi_collapse_single) == 0] <- 'No Barcode'
fam_multi_collapse_difference[lengths(fam_multi_collapse_difference) == 0] <- 'No Barcode'

# Format into metadata so that final lineage determinations can be added to the seurat object
lin_meta_single <- t(as.data.frame(fam_multi_collapse_single))
colnames(lin_meta_single) <- 'final_lineage_single'
rownames(lin_meta_single) <- colnames(df_counts)
all_data$final_lineage_single <- lin_meta_single

lin_meta_difference <- t(as.data.frame(fam_multi_collapse_difference))
colnames(lin_meta_difference) <- 'final_lineage_difference'
rownames(lin_meta_difference) <- colnames(df_counts)
all_data$final_lineage_difference <- lin_meta_difference

```

#Write above to csv
```{r}
table_collapse_single <- table(unlist(fam_multi_collapse_single))
table_collapse_difference <- table(unlist(fam_multi_collapse_difference))

collapse_single_nobarcode <- table_collapse_single[names(table_collapse_single) == 'No Barcode']
collapse_single_stillmultiple <- table_collapse_single[names(table_collapse_single) == 'Still multiple']
collapse_single_single <- length(fam_multi_collapse_single) - collapse_single_nobarcode - collapse_single_stillmultiple
collapse_single <- list(collapse_single_nobarcode, collapse_single_single, collapse_single_stillmultiple)

collapse_difference_nobarcode <- table_collapse_difference[names(table_collapse_difference) == 'No Barcode']
collapse_difference_stillmultiple <- table_collapse_difference[names(table_collapse_difference) == 'Still multiple']
collapse_difference_single <- length(fam_multi_collapse_difference) - collapse_difference_nobarcode - collapse_difference_stillmultiple
collapse_difference <- list(collapse_difference_nobarcode, collapse_difference_single, collapse_difference_stillmultiple)

write.csv(collapse_single, file = "2022_01_14_analysis_scripts/2022_05_27_analysis/Test_barcode_assignment/table_collapse_single.csv")
write.csv(collapse_difference, file = "2022_01_14_analysis_scripts/2022_05_27_analysis/Test_barcode_assignment/    table_collapse_difference.csv")

```
# Seelected collapse_single as the method which keeps highest # of single barcode cells (39011)