---
title: "2022_06_09 AJF009 build_merged_datasets"
output: html_notebook
---

#Set working directory to appropriate folder for inputs and outputs on Google Drive
```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '/Volumes/GoogleDrive/My Drive/Fasse_Shared/AJF_Drive_copy/Experiments/AJF009') # for aria's computer
#knitr::opts_knit$set(root.dir = '/Volumes/GoogleDrive/.shortcut-targets-by-id/1zSqx3IzXMwt6clUjwyqmlOf4G1K53lvy/Fasse_Shared/AJF_Drive_copy/Experiments/AJF009') # for dylan's computer

#2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/ is additional path for outputs
```

# Initialize ----
```{r include = FALSE}
rm(list = ls())
library(dplyr)
library(Seurat)
library(ggplot2)
library(RColorBrewer)

```

# load in GEX data
```{r include = FALSE}

dabtram.data <- Read10X(data.dir = '/2022_05_26_AJF009_counts/2022_05_26_10x_DabTram_counts/outs/filtered_feature_bc_matrix')
cocl2.data <- Read10X(data.dir = '/2022_05_26_AJF009_counts/2022_05_26_10x_CoCl2_counts/outs/filtered_feature_bc_matrix')
cis.data <- Read10X(data.dir = '/2022_05_26_AJF009_counts2022_05_26_10x_Cisplatin_counts/outs/filtered_feature_bc_matrix')

dabtramtodabtram.data <- Read10X(data.dir = '/2022_05_26_AJF009_counts/2022_05_26_10x_DabTramtoDabTram_counts/outs/filtered_feature_bc_matrix')
dabtramtococl2.data <- Read10X(data.dir = '/2022_05_26_AJF009_counts/2022_05_26_10x_DabTramtoCoCl2_counts/outs/filtered_feature_bc_matrix')
dabtramtocis.data <- Read10X(data.dir = '/2022_05_26_AJF009_counts/2022_05_26_10x_DabTramtoCisplatin_counts/outs/filtered_feature_bc_matrix')
cocl2todabtram.data <- Read10X(data.dir = '/2022_05_26_AJF009_counts/2022_05_12_10x_CoCl2toDabTram_counts/outs/filtered_feature_bc_matrix')
cocl2tococl2.data <- Read10X(data.dir = '/2022_05_26_AJF009_counts/2022_05_26_10x_CoCl2toCoCl2_counts/outs/filtered_feature_bc_matrix')
cocl2tocis.data <- Read10X(data.dir = '/2022_05_26_AJF009_counts/2022_05_26_10x_CoCl2toCisplatin_counts/outs/filtered_feature_bc_matrix')
cistodabtram.data <- Read10X(data.dir = '/2022_05_26_AJF009_counts/2022_05_26_10x_CisplatintoDabTram_counts/outs/filtered_feature_bc_matrix')
cistococl2.data <- Read10X(data.dir = '/2022_05_26_AJF009_counts/2022_05_26_10x_CisplatintoCoCl2_counts/outs/filtered_feature_bc_matrix')
cistocis.data <- Read10X(data.dir = '/2022_05_26_AJF009_counts/2022_05_26_10x_CisplatintoCisplatin_counts/outs/filtered_feature_bc_matrix')

```


# convert into Seurat objects
```{r include = FALSE}
dabtram <- CreateSeuratObject(counts = dabtram.data$`Gene Expression`)
cocl2 <- CreateSeuratObject(counts = cocl2.data$`Gene Expression`)
cis <- CreateSeuratObject(counts = cis.data$`Gene Expression`)
dabtramtodabtram <- CreateSeuratObject(counts = dabtramtodabtram.data$`Gene Expression`)
dabtramtococl2 <- CreateSeuratObject(counts = dabtramtococl2.data$`Gene Expression`)
dabtramtocis <- CreateSeuratObject(counts = dabtramtocis.data$`Gene Expression`)
cocl2todabtram <- CreateSeuratObject(counts = cocl2todabtram.data$`Gene Expression`)
cocl2tococl2 <- CreateSeuratObject(counts = cocl2tococl2.data$`Gene Expression`)
cocl2tocis <- CreateSeuratObject(counts = cocl2tocis.data$`Gene Expression`)
cistodabtram <- CreateSeuratObject(counts = cistodabtram.data$`Gene Expression`)
cistococl2 <- CreateSeuratObject(counts = cistococl2.data$`Gene Expression`)
cistocis <- CreateSeuratObject(counts = cistocis.data$`Gene Expression`)

```


# Find the number of cells in each condition prior to filtering
```{r}
starting_num_cells <- c(dabtram = ncol(dabtram),
                        cocl2 = ncol(cocl2),
                        cis = ncol(cis),
                        dabtramtodabtram = ncol(dabtramtodabtram),
                        dabtramtococl2 = ncol(dabtramtococl2),
                        dabtramtocis = ncol(dabtramtocis),
                        cocl2todabtram = ncol(cocl2todabtram),
                        cocl2tococl2 = ncol(cocl2tococl2),
                        cocl2tocis = ncol(cocl2tocis),
                        cistodabtram = ncol(cistodabtram),
                        cistococl2 = ncol(cistococl2),
                        cistocis = ncol(cistocis)
                        )
```

# Add lineage data to the seurat object
```{r}
dabtram[['lineage']] <- CreateAssayObject(counts = dabtram.data$Custom, min.cells = 1)
cocl2[['lineage']] <- CreateAssayObject(counts = cocl2.data$Custom, min.cells = 1)
cis[['lineage']] <- CreateAssayObject(counts = cis.data$Custom, min.cells = 1)
dabtramtodabtram[['lineage']] <- CreateAssayObject(counts = dabtramtodabtram.data$Custom, min.cells = 1)
dabtramtococl2[['lineage']] <- CreateAssayObject(counts = dabtramtococl2.data$Custom, min.cells = 1)
dabtramtocis[['lineage']] <- CreateAssayObject(counts = dabtramtocis.data$Custom, min.cells = 1)
cocl2todabtram[['lineage']] <- CreateAssayObject(counts = cocl2todabtram.data$Custom, min.cells = 1)
cocl2tococl2[['lineage']] <- CreateAssayObject(counts = cocl2tococl2.data$Custom, min.cells = 1)
cocl2tocis[['lineage']] <- CreateAssayObject(counts = cocl2tocis.data$Custom, min.cells = 1)
cistodabtram[['lineage']] <- CreateAssayObject(counts = cistodabtram.data$Custom, min.cells = 1)
cistococl2[['lineage']] <- CreateAssayObject(counts = cistococl2.data$Custom, min.cells = 1)
cistocis[['lineage']] <- CreateAssayObject(counts = cistocis.data$Custom, min.cells = 1)
```

# Determine ribosomal and mitochondrial gene counts for each condition
```{r include = FALSE}
dabtram[["percent.mt"]] <- PercentageFeatureSet(object = dabtram, pattern = "^MT-")
dabtram[["percent.rb"]] <- PercentageFeatureSet(object = dabtram, pattern = "^RPS")

cocl2[["percent.mt"]] <- PercentageFeatureSet(object = cocl2, pattern = "^MT-")
cocl2[["percent.rb"]] <- PercentageFeatureSet(object = cocl2, pattern = "^RPS")

cis[["percent.mt"]] <- PercentageFeatureSet(object = cis, pattern = "^MT-")
cis[["percent.rb"]] <- PercentageFeatureSet(object = cis, pattern = "^RPS")

dabtramtodabtram[["percent.mt"]] <- PercentageFeatureSet(object = dabtramtodabtram, pattern = "^MT-")
dabtramtodabtram[["percent.rb"]] <- PercentageFeatureSet(object = dabtramtodabtram, pattern = "^RPS")

dabtramtococl2[["percent.mt"]] <- PercentageFeatureSet(object = dabtramtococl2, pattern = "^MT-")
dabtramtococl2[["percent.rb"]] <- PercentageFeatureSet(object = dabtramtococl2, pattern = "^RPS")

dabtramtocis[["percent.mt"]] <- PercentageFeatureSet(object = dabtramtocis, pattern = "^MT-")
dabtramtocis[["percent.rb"]] <- PercentageFeatureSet(object = dabtramtocis, pattern = "^RPS")

cocl2todabtram[["percent.mt"]] <- PercentageFeatureSet(object = cocl2todabtram, pattern = "^MT-")
cocl2todabtram[["percent.rb"]] <- PercentageFeatureSet(object = cocl2todabtram, pattern = "^RPS")

cocl2tococl2[["percent.mt"]] <- PercentageFeatureSet(object = cocl2tococl2, pattern = "^MT-")
cocl2tococl2[["percent.rb"]] <- PercentageFeatureSet(object = cocl2tococl2, pattern = "^RPS")

cocl2tocis[["percent.mt"]] <- PercentageFeatureSet(object = cocl2tocis, pattern = "^MT-")
cocl2tocis[["percent.rb"]] <- PercentageFeatureSet(object = cocl2tocis, pattern = "^RPS")

cistodabtram[["percent.mt"]] <- PercentageFeatureSet(object = cistodabtram, pattern = "^MT-")
cistodabtram[["percent.rb"]] <- PercentageFeatureSet(object = cistodabtram, pattern = "^RPS")

cistococl2[["percent.mt"]] <- PercentageFeatureSet(object = cistococl2, pattern = "^MT-")
cistococl2[["percent.rb"]] <- PercentageFeatureSet(object = cistococl2, pattern = "^RPS")

cistocis[["percent.mt"]] <- PercentageFeatureSet(object = cistocis, pattern = "^MT-")
cistocis[["percent.rb"]] <- PercentageFeatureSet(object = cistocis, pattern = "^RPS")
```

# Plot QC metrics
```{r}
VlnPlot(object = dabtram, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
FeatureScatter(object = dabtram, feature1 = "nCount_RNA", feature2 = "percent.mt") 
FeatureScatter(object = dabtram, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

VlnPlot(object = cocl2, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
FeatureScatter(object = cocl2, feature1 = "nCount_RNA", feature2 = "percent.mt") 
FeatureScatter(object = cocl2, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

VlnPlot(object = cis, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
FeatureScatter(object = cis, feature1 = "nCount_RNA", feature2 = "percent.mt") 
FeatureScatter(object = cis, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

VlnPlot(object = dabtramtodabtram, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
FeatureScatter(object = dabtramtodabtram, feature1 = "nCount_RNA", feature2 = "percent.mt") 
FeatureScatter(object = dabtramtodabtram, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

VlnPlot(object = dabtramtococl2, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
FeatureScatter(object = dabtramtococl2, feature1 = "nCount_RNA", feature2 = "percent.mt") 
FeatureScatter(object = dabtramtococl2, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

VlnPlot(object = dabtramtocis, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
FeatureScatter(object = dabtramtocis, feature1 = "nCount_RNA", feature2 = "percent.mt") 
FeatureScatter(object = dabtramtocis, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

VlnPlot(object = cocl2todabtram, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
FeatureScatter(object = cocl2todabtram, feature1 = "nCount_RNA", feature2 = "percent.mt") 
FeatureScatter(object = cocl2todabtram, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

VlnPlot(object = cocl2tococl2, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
FeatureScatter(object = cocl2tococl2, feature1 = "nCount_RNA", feature2 = "percent.mt") 
FeatureScatter(object = cocl2tococl2, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

VlnPlot(object = cocl2tocis, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
FeatureScatter(object = cocl2tocis, feature1 = "nCount_RNA", feature2 = "percent.mt") 
FeatureScatter(object = cocl2tocis, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

VlnPlot(object = cistodabtram, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
FeatureScatter(object = cistodabtram, feature1 = "nCount_RNA", feature2 = "percent.mt") 
FeatureScatter(object = cistodabtram, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

VlnPlot(object = cistococl2, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
FeatureScatter(object = cistococl2, feature1 = "nCount_RNA", feature2 = "percent.mt") 
FeatureScatter(object = cistococl2, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

VlnPlot(object = cistocis, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
FeatureScatter(object = cistocis, feature1 = "nCount_RNA", feature2 = "percent.mt") 
FeatureScatter(object = cistocis, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")

```

# filter based on above parameters to remove low quality cells and outliers and replot, note percentage of cells kept after filtering
```{r}
dabtram_onc <- dabtram@assays$lineage@counts@Dim[2]
dabtram <- subset(x = dabtram, subset = nFeature_RNA > 1000 & nCount_RNA < 50000 & percent.mt < 15)
VlnPlot(object = dabtram, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
#percent of cells kept after this filter
dabtram_f1 <- dabtram@assays$lineage@counts@Dim[2]/dabtram_onc
print(dabtram_f1*100)

cocl2_onc <- cocl2@assays$lineage@counts@Dim[2]
cocl2 <- subset(x = cocl2, subset = nFeature_RNA > 1000 & nCount_RNA < 30000 & percent.mt < 20)
VlnPlot(object = cocl2, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
#percent of cells kept after this filter
cocl2_f1 <- cocl2@assays$lineage@counts@Dim[2]/cocl2_onc
print(cocl2_f1*100)

cis_onc <- cis@assays$lineage@counts@Dim[2]
cis <- subset(x = cis, subset = nFeature_RNA > 500 & nCount_RNA < 30000 & percent.mt < 25) #
VlnPlot(object = cis, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
#percent of cells kept after this filter
cis_f1 <- cis@assays$lineage@counts@Dim[2]/cis_onc
print(cis_f1*100)

dabtramtodabtram_onc <- dabtramtodabtram@assays$lineage@counts@Dim[2]
dabtramtodabtram <- subset(x = dabtramtodabtram, subset = nFeature_RNA > 1000 & nCount_RNA < 20000 & percent.mt < 15)
VlnPlot(object = dabtramtodabtram, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
#percent of cells kept after this filter
dabtramtodabtram_f1 <- dabtramtodabtram@assays$lineage@counts@Dim[2]/dabtramtodabtram_onc
print(dabtramtodabtram_f1*100)

dabtramtococl2_onc <- dabtramtococl2@assays$lineage@counts@Dim[2]
dabtramtococl2 <- subset(x = dabtramtococl2, subset = nFeature_RNA > 500 & nCount_RNA < 30000 & percent.mt < 20)
VlnPlot(object = dabtramtococl2, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
#percent of cells kept after this filter
dabtramtococl2_f1 <- dabtramtococl2@assays$lineage@counts@Dim[2]/dabtramtococl2_onc
print(dabtramtococl2_f1*100)

dabtramtocis_onc <- dabtramtocis@assays$lineage@counts@Dim[2]
dabtramtocis <- subset(x = dabtramtocis, subset = nFeature_RNA > 500 & nCount_RNA < 20000 & percent.mt < 25)
VlnPlot(object = dabtramtocis, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
#percent of cells kept after this filter
dabtramtocis_f1 <- dabtramtocis@assays$lineage@counts@Dim[2]/dabtramtocis_onc
print(dabtramtocis_f1*100)

cocl2todabtram_onc <- cocl2todabtram@assays$lineage@counts@Dim[2]
cocl2todabtram <- subset(x = cocl2todabtram, subset = nFeature_RNA > 1000 & nCount_RNA < 60000 & percent.mt < 15)
VlnPlot(object = cocl2todabtram, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
#percent of cells kept after this filter
cocl2todabtram_f1 <- cocl2todabtram@assays$lineage@counts@Dim[2]/cocl2todabtram_onc
print(cocl2todabtram_f1*100)

cocl2tococl2_onc <- cocl2tococl2@assays$lineage@counts@Dim[2]
cocl2tococl2 <- subset(x = cocl2tococl2, subset = nFeature_RNA > 500 & nCount_RNA < 30000 & percent.mt < 25)
VlnPlot(object = cocl2tococl2, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
#percent of cells kept after this filter
cocl2tococl2_f1 <- cocl2tococl2@assays$lineage@counts@Dim[2]/cocl2tococl2_onc
print(cocl2tococl2_f1*100)

cocl2tocis_onc <- cocl2tocis@assays$lineage@counts@Dim[2]
cocl2tocis <- subset(x = cocl2tocis, subset = nFeature_RNA > 500 & nCount_RNA < 20000 & percent.mt < 25)
VlnPlot(object = cocl2tocis, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
#percent of cells kept after this filter
cocl2tocis_f1 <- cocl2tocis@assays$lineage@counts@Dim[2]/cocl2tocis_onc
print(cocl2tocis_f1*100)

cistodabtram_onc <- cistodabtram@assays$lineage@counts@Dim[2]
cistodabtram <- subset(x = cistodabtram, subset = nFeature_RNA > 500 & nCount_RNA < 35000 & percent.mt < 15) #
VlnPlot(object = cistodabtram, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
#percent of cells kept after this filter
cistodabtram_f1 <- cistodabtram@assays$lineage@counts@Dim[2]/cistodabtram_onc
print(cistodabtram_f1*100)

cistococl2_onc <- cistococl2@assays$lineage@counts@Dim[2]
cistococl2 <- subset(x = cistococl2, subset = nFeature_RNA > 500 & nCount_RNA < 30000 & percent.mt < 20) #
VlnPlot(object = cistococl2, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
#percent of cells kept after this filter
cistococl2_f1 <- cistococl2@assays$lineage@counts@Dim[2]/cistococl2_onc
print(cistococl2_f1*100)

cistocis_onc <- cistocis@assays$lineage@counts@Dim[2]
cistocis <- subset(x = cistocis, subset = nFeature_RNA > 1000 & nCount_RNA < 30000 & percent.mt < 20) #
VlnPlot(object = cistocis, features = c("nFeature_RNA", "nCount_RNA", "percent.mt", "percent.rb"), ncol = 4)
#percent of cells kept after this filter
cistocis_f1 <- cistocis@assays$lineage@counts@Dim[2]/cistocis_onc
print(cistocis_f1*100)
```

# Find number of cells per condition post filter
```{r}

postfilt_num_cells <- c(dabtram = ncol(dabtram),
                        cocl2 = ncol(cocl2),
                        cis = ncol(cis),
                        dabtramtodabtram = ncol(dabtramtodabtram),
                        dabtramtococl2 = ncol(dabtramtococl2),
                        dabtramtocis = ncol(dabtramtocis),
                        cocl2todabtram = ncol(cocl2todabtram),
                        cocl2tococl2 = ncol(cocl2tococl2),
                        cocl2tocis = ncol(cocl2tocis),
                        cistodabtram = ncol(cistodabtram),
                        cistococl2 = ncol(cistococl2),
                        cistocis = ncol(cistocis))

df <- data.frame(starting = starting_num_cells, post_filt = postfilt_num_cells, percent = postfilt_num_cells/starting_num_cells)
write.csv(df, '2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/cellsPreandPostFilt.csv')
rm(df)

```

# Remove unnecesary files
```{r}

rm(list = c('dabtram.data',
            'dabtram_f1',
            'dabtram_onc',
            'cocl2.data',
            'cocl2_f1',
            'cocl2_onc',
            'cis.data',
            'cis_f1',
            'cis_onc',
            'dabtramtodabtram.data',
            'dabtramtodabtram_f1',
            'dabtramtodabtram_onc',
            'dabtramtococl2.data',
            'dabtramtococl2_f1',
            'dabtramtococl2_onc',
            'dabtramtocis.data',
            'dabtramtocis_f1',
            'dabtramtocis_onc',
            'cocl2todabtram.data',
            'cocl2todabtram_f1',
            'cocl2todabtram_onc',
            'cocl2tococl2.data',
            'cocl2tococl2_f1',
            'cocl2tococl2_onc',
            'cocl2tocis.data',
            'cocl2tocis_f1',
            'cocl2tocis_onc',
            'cistodabtram.data',
            'cistodabtram_f1',
            'cistodabtram_onc',
            'cistococl2.data',
            'cistococl2_f1',
            'cistococl2_onc',
            'cistocis.data',
            'cistocis_f1',
            'cistocis_onc',
            'postfilt_num_cells',
            'starting_num_cells'))
```

# Allow R to use more memory
```{r}
options(future.globals.maxSize= 35 * 1024^2)
```

#Normalize and identify variable features
```{r include = FALSE}

dabtram <- dabtram %>% Seurat::NormalizeData(verbose = FALSE) %>% FindVariableFeatures(selection.method = "vst", nfeatures = 20000) %>%  ScaleData(verbose = FALSE) %>% RunPCA(verbose = FALSE)
cocl2 <- cocl2 %>% Seurat::NormalizeData(verbose = FALSE) %>% FindVariableFeatures(selection.method = "vst", nfeatures = 20000) %>%  ScaleData(verbose = FALSE) %>% RunPCA(verbose = FALSE)
cis <- cis %>% Seurat::NormalizeData(verbose = FALSE) %>% FindVariableFeatures(selection.method = "vst", nfeatures = 20000) %>%  ScaleData(verbose = FALSE) %>% RunPCA(verbose = FALSE)
dabtramtodabtram <- dabtramtodabtram %>% Seurat::NormalizeData(verbose = FALSE) %>% FindVariableFeatures(selection.method = "vst", nfeatures = 20000) %>%  ScaleData(verbose = FALSE) %>% RunPCA(verbose = FALSE)
dabtramtococl2 <- dabtramtococl2 %>% Seurat::NormalizeData(verbose = FALSE) %>% FindVariableFeatures(selection.method = "vst", nfeatures = 20000) %>%  ScaleData(verbose = FALSE) %>% RunPCA(verbose = FALSE)
dabtramtocis <- dabtramtocis %>% Seurat::NormalizeData(verbose = FALSE) %>% FindVariableFeatures(selection.method = "vst", nfeatures = 20000) %>%  ScaleData(verbose = FALSE) %>% RunPCA(verbose = FALSE)
cocl2todabtram <- cocl2todabtram %>% Seurat::NormalizeData(verbose = FALSE) %>% FindVariableFeatures(selection.method = "vst", nfeatures = 20000) %>%  ScaleData(verbose = FALSE) %>% RunPCA(verbose = FALSE)
cocl2tococl2 <- cocl2tococl2 %>% Seurat::NormalizeData(verbose = FALSE) %>% FindVariableFeatures(selection.method = "vst", nfeatures = 20000) %>%  ScaleData(verbose = FALSE) %>% RunPCA(verbose = FALSE)
cocl2tocis <- cocl2tocis %>% Seurat::NormalizeData(verbose = FALSE) %>% FindVariableFeatures(selection.method = "vst", nfeatures = 20000) %>%  ScaleData(verbose = FALSE) %>% RunPCA(verbose = FALSE)
cistodabtram <- cistodabtram %>% Seurat::NormalizeData(verbose = FALSE) %>% FindVariableFeatures(selection.method = "vst", nfeatures = 20000) %>%  ScaleData(verbose = FALSE) %>% RunPCA(verbose = FALSE)
cistococl2 <- cistococl2 %>% Seurat::NormalizeData(verbose = FALSE) %>% FindVariableFeatures(selection.method = "vst", nfeatures = 20000) %>%  ScaleData(verbose = FALSE) %>% RunPCA(verbose = FALSE)
cistocis <- cistocis %>% Seurat::NormalizeData(verbose = FALSE) %>% FindVariableFeatures(selection.method = "vst", nfeatures = 20000) %>%  ScaleData(verbose = FALSE) %>% RunPCA(verbose = FALSE)

```

# Add cell cycle scores
```{r include = FALSE}
dabtram <- CellCycleScoring(object = dabtram, g2m.features = cc.genes$g2m.genes, s.features = cc.genes$s.genes)
cocl2 <- CellCycleScoring(object = cocl2, g2m.features = cc.genes$g2m.genes, s.features = cc.genes$s.genes)
cis <- CellCycleScoring(object = cis, g2m.features = cc.genes$g2m.genes, s.features = cc.genes$s.genes)
dabtramtodabtram <- CellCycleScoring(object = dabtramtodabtram, g2m.features = cc.genes$g2m.genes, s.features = cc.genes$s.genes)
dabtramtococl2 <- CellCycleScoring(object = dabtramtococl2, g2m.features = cc.genes$g2m.genes, s.features = cc.genes$s.genes)
dabtramtocis <- CellCycleScoring(object = dabtramtocis, g2m.features = cc.genes$g2m.genes, s.features = cc.genes$s.genes)
cocl2todabtram <- CellCycleScoring(object = cocl2todabtram, g2m.features = cc.genes$g2m.genes, s.features = cc.genes$s.genes)
cocl2tococl2 <- CellCycleScoring(object = cocl2tococl2, g2m.features = cc.genes$g2m.genes, s.features = cc.genes$s.genes)
cocl2tocis <- CellCycleScoring(object = cocl2tocis, g2m.features = cc.genes$g2m.genes, s.features = cc.genes$s.genes)
cistodabtram <- CellCycleScoring(object = cistodabtram, g2m.features = cc.genes$g2m.genes, s.features = cc.genes$s.genes)
cistococl2 <- CellCycleScoring(object = cistococl2, g2m.features = cc.genes$g2m.genes, s.features = cc.genes$s.genes)
cistocis <- CellCycleScoring(object = cistocis, g2m.features = cc.genes$g2m.genes, s.features = cc.genes$s.genes)

```

# Run UMAP
```{r include = FALSE}

dabtram <- FindNeighbors(object = dabtram, dims = c(1:20))
dabtram <- FindClusters(object = dabtram, resolution = .5)
dabtram <- RunUMAP(object = dabtram, dims = c(1:20))

cocl2 <- FindNeighbors(object = cocl2, dims = c(1:20))
cocl2 <- FindClusters(object = cocl2, resolution = .5)
cocl2 <- RunUMAP(object = cocl2, dims = c(1:20))

cis <- FindNeighbors(object = cis, dims = c(1:20))
cis <- FindClusters(object = cis, resolution = .5)
cis <- RunUMAP(object = cis, dims = c(1:20))

dabtramtodabtram <- FindNeighbors(object = dabtramtodabtram, dims = c(1:20))
dabtramtodabtram <- FindClusters(object = dabtramtodabtram, resolution = .5)
dabtramtodabtram <- RunUMAP(object = dabtramtodabtram, dims = c(1:20))

dabtramtococl2 <- FindNeighbors(object = dabtramtococl2, dims = c(1:20))
dabtramtococl2 <- FindClusters(object = dabtramtococl2, resolution = .5)
dabtramtococl2 <- RunUMAP(object = dabtramtococl2, dims = c(1:20))

dabtramtocis <- FindNeighbors(object = dabtramtocis, dims = c(1:20))
dabtramtocis <- FindClusters(object = dabtramtocis, resolution = .5)
dabtramtocis <- RunUMAP(object = dabtramtocis, dims = c(1:20))

cocl2todabtram <- FindNeighbors(object = cocl2todabtram, dims = c(1:20))
cocl2todabtram <- FindClusters(object = cocl2todabtram, resolution = .5)
cocl2todabtram <- RunUMAP(object = cocl2todabtram, dims = c(1:20))

cocl2tococl2 <- FindNeighbors(object = cocl2tococl2, dims = c(1:20))
cocl2tococl2 <- FindClusters(object = cocl2tococl2, resolution = .5)
cocl2tococl2 <- RunUMAP(object = cocl2tococl2, dims = c(1:20))

cocl2tocis <- FindNeighbors(object = cocl2tocis, dims = c(1:20))
cocl2tocis <- FindClusters(object = cocl2tocis, resolution = .5)
cocl2tocis <- RunUMAP(object = cocl2tocis, dims = c(1:20))

cistodabtram <- FindNeighbors(object = cistodabtram, dims = c(1:20))
cistodabtram <- FindClusters(object = cistodabtram, resolution = .5)
cistodabtram <- RunUMAP(object = cistodabtram, dims = c(1:20))

cistococl2 <- FindNeighbors(object = cistococl2, dims = c(1:20))
cistococl2 <- FindClusters(object = cistococl2, resolution = .5)
cistococl2 <- RunUMAP(object = cistococl2, dims = c(1:20))

cistocis <- FindNeighbors(object = cistocis, dims = c(1:20))
cistocis <- FindClusters(object = cistocis, resolution = .5)
cistocis <- RunUMAP(object = cistocis, dims = c(1:20))

```

# Plot UMAP clusters
```{r include = FALSE}

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/DabTram_UMAP_clusters.pdf')
DimPlot(dabtram, reduction = "umap",dims = c(1,2), group.by = 'seurat_clusters', pt.size = 1) + ggtitle('Seurat Clusters DabTram')
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CoCl2_UMAP_clusters.pdf')
DimPlot(cocl2, reduction = "umap",dims = c(1,2), group.by = 'seurat_clusters', pt.size = 1) + ggtitle('Seurat Clusters CoCl2')
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/Cis_UMAP_clusters.pdf')
DimPlot(cis, reduction = "umap",dims = c(1,2), group.by = 'seurat_clusters', pt.size = 1) + ggtitle('Seurat Clusters Cis')
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/DabTramtoDabTram_UMAP_clusters.pdf')
DimPlot(dabtramtodabtram, reduction = "umap",dims = c(1,2), group.by = 'seurat_clusters', pt.size = 1) + ggtitle('Seurat Clusters DabTram to DabTram')
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/DabTramtoCoCl2_UMAP_clusters.pdf')
DimPlot(dabtramtococl2, reduction = "umap",dims = c(1,2), group.by = 'seurat_clusters', pt.size = 1) + ggtitle('Seurat Clusters DabTram to CoCl2')
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/DabTramtoCis_UMAP_clusters.pdf')
DimPlot(dabtramtocis, reduction = "umap",dims = c(1,2), group.by = 'seurat_clusters', pt.size = 1) + ggtitle('Seurat Clusters DabTram to Cis')
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CoCl2toDabTram_UMAP_clusters.pdf')
DimPlot(cocl2todabtram, reduction = "umap",dims = c(1,2), group.by = 'seurat_clusters', pt.size = 1) + ggtitle('Seurat Clusters CoCl2 to DabTram')
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CoCl2toCoCl2_UMAP_clusters.pdf')
DimPlot(cocl2tococl2, reduction = "umap",dims = c(1,2), group.by = 'seurat_clusters', pt.size = 1) + ggtitle('Seurat Clusters CoCl2 to CoCl2')
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CoCl2toCis_UMAP_clusters.pdf')
DimPlot(cocl2tocis, reduction = "umap",dims = c(1,2), group.by = 'seurat_clusters', pt.size = 1) + ggtitle('Seurat Clusters CoCl2 to Cis')
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CistoDabTram_UMAP_clusters.pdf')
DimPlot(cistodabtram, reduction = "umap",dims = c(1,2), group.by = 'seurat_clusters', pt.size = 1) + ggtitle('Seurat Clusters Cis to DabTram')
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CistoCoCl2_UMAP_clusters.pdf')
DimPlot(cistococl2, reduction = "umap",dims = c(1,2), group.by = 'seurat_clusters', pt.size = 1) + ggtitle('Seurat Clusters Cis to CoCl2')
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CistoCis_UMAP_clusters.pdf')
DimPlot(cistocis, reduction = "umap",dims = c(1,2), group.by = 'seurat_clusters', pt.size = 1) + ggtitle('Seurat Clusters Cis to Cis')
dev.off()

```

# Make sure assay is always RNA
```{r include = FALSE}
DefaultAssay(object = dabtram) <- "RNA"
DefaultAssay(object = cocl2) <- "RNA"
DefaultAssay(object = cis) <- "RNA"
DefaultAssay(object = dabtramtodabtram) <- "RNA"
DefaultAssay(object = dabtramtococl2) <- "RNA"
DefaultAssay(object = dabtramtocis) <- "RNA"
DefaultAssay(object = cocl2todabtram) <- "RNA"
DefaultAssay(object = cocl2tococl2) <- "RNA"
DefaultAssay(object = cocl2tocis) <- "RNA"
DefaultAssay(object = cistodabtram) <- "RNA"
DefaultAssay(object = cistococl2) <- "RNA"
DefaultAssay(object = cistocis) <- "RNA"

```

# Plot marker genes and save as PDFs
```{r include = FALSE}

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/DabTram_UMAP_markers.pdf')
FeaturePlot(object = dabtram, reduction = 'umap',features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) 
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CoCl2_UMAP_markers.pdf')
FeaturePlot(object = cocl2, reduction = 'umap',features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) 
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/Cis_UMAP_markers.pdf')
FeaturePlot(object = cis, reduction = 'umap',features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) 
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/DabTramtoDabTram_UMAP_markers.pdf')
FeaturePlot(object = dabtramtodabtram, reduction = 'umap',features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) 
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/DabTramtoCoCl2_UMAP_markers.pdf')
FeaturePlot(object = dabtramtococl2, reduction = 'umap',features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) 
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/DabTramtoCis_UMAP_markers.pdf')
FeaturePlot(object = dabtramtocis, reduction = 'umap',features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) 
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CoCl2toDabTram_UMAP_markers.pdf')
FeaturePlot(object = cocl2todabtram, reduction = 'umap',features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) 
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CoCl2toCoCl2_UMAP_markers.pdf')
FeaturePlot(object = cocl2tococl2, reduction = 'umap',features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) 
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CoCl2toCis_UMAP_markers.pdf')
FeaturePlot(object = cocl2tocis, reduction = 'umap',features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) 
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CistoDabTram_UMAP_markers.pdf')
FeaturePlot(object = cistodabtram, reduction = 'umap',features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) 
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CistoCoCl2_UMAP_markers.pdf')
FeaturePlot(object = cistococl2, reduction = 'umap',features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) 
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/CistoCis_UMAP_markers.pdf')
FeaturePlot(object = cistocis, reduction = 'umap',features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) 
dev.off()

```

# Save individual objects prior to merging
```{r include = FALSE}
save(dabtram, cocl2, cis, dabtramtodabtram, dabtramtococl2, dabtramtocis, cocl2todabtram, cocl2tococl2, cocl2tocis, cistodabtram, cistococl2, cistocis, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/Objects_premerged.RData')
```

# Merge the data!! merge.data = T to maintain normalization of each object
```{r include = FALSE}
all_data <- merge(dabtram, y = c(cocl2, cis, dabtramtodabtram, dabtramtococl2, dabtramtocis, cocl2todabtram, cocl2tococl2, cocl2tocis, cistodabtram, cistococl2, cistocis), add.cell.ids = c("dabtram", "cocl2", "cis", "dabtramtodabtram", "dabtramtococl2", "dabtramtocis", "cocl2todabtram", "cocl2tococl2", "cocl2tocis", "cistodabtram", "cistococl2", "cistocis"), project = "All_Data", merge.data = T)
```

# Merge for smaller UMAPS, all first timepoint, all second timepoint, dabtram at each time point
```{r include = FALSE}
first_timepoint <- merge(dabtram, y = c(cocl2, cis), add.cell.ids = c("dabtram", "cocl2", "cis"), project = "first_timepoint", merge.data = T)

second_timepoint <- merge(dabtramtodabtram, y = c(dabtramtococl2, dabtramtocis, cocl2todabtram, cocl2tococl2, cocl2tocis, cistodabtram, cistococl2, cistocis), add.cell.ids = c("dabtramtodabtram", "dabtramtococl2", "dabtramtocis", "cocl2todabtram", "cocl2tococl2", "cocl2tocis", "cistodabtram", "cistococl2", "cistocis"), project = "second_timepoint", merge.data = T)

dabtram_both_times <- merge(dabtram, y = dabtramtodabtram, add.cell.ids = c("dabtram", "dabtramtodabtram"), project = "All_Data", merge.data = T)

```

# Save merged data, remove individual objects
``` {r include = FALSE}
save(all_data, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/Object_postmerge.RData')
save(first_timepoint, second_timepoint, dabtram_both_times, file = "2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/timepoint_separated_postmerge.RData")
rm(dabtram, cocl2, cis, dabtramtodabtram, dabtramtococl2, dabtramtocis, cocl2todabtram, cocl2tococl2, cocl2tocis, cistodabtram, cistococl2, cistocis, postfilt_num_cells, starting_num_cells) 
```

# Scale, run PCA and UMAP, save
```{r include = FALSE}
all_data <- FindVariableFeatures(all_data) %>% ScaleData() %>% RunPCA(verbose=FALSE) %>% RunUMAP(dims = 1:20, verbose = FALSE) %>% FindNeighbors(dims = 1:20, verbose = FALSE) %>%  FindClusters(resolution = 0.3)
DimPlot(all_data)

#0.3 resolution results in 12 clusters
#rm(all_data)

condition <- c()
for (i in 1:length(all_data@assays$RNA@counts@Dimnames[2][[1]])){
  condition <- rbind(condition, strsplit(all_data@assays$RNA@counts@Dimnames[2][[1]][[i]], '_')[[1]][1])
}
all_data$OG_condition <- condition
save(all_data, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/all_data_merged.RData')

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/all_data_merged.pdf')
print(DimPlot(all_data))
print(DimPlot(all_data, label = T, group.by = 'OG_condition', cols = c('dabtram' = '#623594', 'cocl2' = '#0F8241', 'cis' = '#C96D29', 'dabtramtodabtram' = '#561E59', 'dabtramtococl2' = '#A2248E', 'dabtramtocis' = '#9D85BE', 'cocl2todabtram' = '#10413B', 'cocl2tococl2' = '#6ABD45', 'cocl2tocis' = '#6DC49C', 'cistodabtram' = '#A23622', 'cistococl2' = '#F49129', 'cistocis' = '#FBD08C')))
print(FeaturePlot(object = all_data, reduction = 'umap', features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) & scale_colour_gradientn(colors = rev(brewer.pal(n = 11, name = 'RdBu'))))
dev.off()

```

# Scale, run PCA and UMAP, save
```{r include = FALSE}
first_timepoint <- FindVariableFeatures(first_timepoint) %>% ScaleData() %>% RunPCA(verbose=FALSE) %>% RunUMAP(dims = 1:20, verbose = FALSE) %>% FindNeighbors(dims = 1:20, verbose = FALSE) %>%  FindClusters(resolution = 0.4)
DimPlot(first_timepoint)

condition <- c()
for (i in 1:length(first_timepoint@assays$RNA@counts@Dimnames[2][[1]])){
  condition <- rbind(condition, strsplit(first_timepoint@assays$RNA@counts@Dimnames[2][[1]][[i]], '_')[[1]][1])
}
first_timepoint$OG_condition <- condition
save(first_timepoint, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/first_timepoint_merged.RData')

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/first_timepoint_merged.pdf')
print(DimPlot(first_timepoint))
print(DimPlot(first_timepoint, label = T, group.by = 'OG_condition', cols = c('dabtram' = '#623594', 'cocl2' = '#0F8241', 'cis' = '#C96D29')))
print(FeaturePlot(object = first_timepoint, reduction = 'umap', features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) & scale_colour_gradientn(colors = rev(brewer.pal(n = 11, name = 'RdBu'))))
dev.off()

```

# Scale, run PCA and UMAP, save
```{r include = FALSE}
second_timepoint <- FindVariableFeatures(second_timepoint) %>% ScaleData() %>% RunPCA(verbose=FALSE) %>% RunUMAP(dims = 1:20, verbose = FALSE) %>% FindNeighbors(dims = 1:20, verbose = FALSE) %>%  FindClusters(resolution = 0.4)
DimPlot(second_timepoint)

condition <- c()
for (i in 1:length(second_timepoint@assays$RNA@counts@Dimnames[2][[1]])){
  condition <- rbind(condition, strsplit(second_timepoint@assays$RNA@counts@Dimnames[2][[1]][[i]], '_')[[1]][1])
}
second_timepoint$OG_condition <- condition
save(second_timepoint, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/second_timepoint_merged.RData')

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/second_timepoint_merged.pdf')
print(DimPlot(second_timepoint))
print(DimPlot(second_timepoint, label = T, group.by = 'OG_condition', cols = c('dabtramtodabtram' = '#561E59', 'dabtramtococl2' = '#A2248E', 'dabtramtocis' = '#9D85BE', 'cocl2todabtram' = '#10413B', 'cocl2tococl2' = '#6ABD45', 'cocl2tocis' = '#6DC49C', 'cistodabtram' = '#A23622', 'cistococl2' = '#F49129', 'cistocis' = '#FBD08C')))
print(FeaturePlot(object = second_timepoint, reduction = 'umap', features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) & scale_colour_gradientn(colors = rev(brewer.pal(n = 11, name = 'RdBu'))))
dev.off()

```

# Scale, run PCA and UMAP, save
```{r include = FALSE}
dabtram_both_times <- FindVariableFeatures(dabtram_both_times) %>% ScaleData() %>% RunPCA(verbose=FALSE) %>% RunUMAP(dims = 1:20, verbose = FALSE) %>% FindNeighbors(dims = 1:20, verbose = FALSE) %>%  FindClusters(resolution = 0.015)
DimPlot(dabtram_both_times)

#0.3 resolution results in 12 clusters
#rm(all_data)

condition <- c()
for (i in 1:length(dabtram_both_times@assays$RNA@counts@Dimnames[2][[1]])){
  condition <- rbind(condition, strsplit(dabtram_both_times@assays$RNA@counts@Dimnames[2][[1]][[i]], '_')[[1]][1])
}
dabtram_both_times$OG_condition <- condition
save(dabtram_both_times, file = '2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/dabtram_both_times.RData')

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/dabtram_both_times.pdf')
print(DimPlot(dabtram_both_times))
print(DimPlot(dabtram_both_times, label = T, group.by = 'OG_condition', cols = c('dabtram' = '#623594', 'cocl2' = '#0F8241', 'cis' = '#C96D29', 'dabtramtodabtram' = '#561E59', 'dabtramtococl2' = '#A2248E', 'dabtramtocis' = '#9D85BE', 'cocl2todabtram' = '#10413B', 'cocl2tococl2' = '#6ABD45', 'cocl2tocis' = '#6DC49C', 'cistodabtram' = '#A23622', 'cistococl2' = '#F49129', 'cistocis' = '#FBD08C')))
print(FeaturePlot(object = dabtram_both_times, reduction = 'umap', features = c("NGFR","EGFR","AXL","NT5E","FN1","SERPINE2","MITF","nFeature_RNA","nCount_RNA"), pt.size = 1, combine = T, order = TRUE) & scale_colour_gradientn(colors = rev(brewer.pal(n = 11, name = 'RdBu'))))
dev.off()

```